---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.height=6, fig.width=8)
```

# Packages

```{r, message=FALSE, warning=FALSE}
pacman::p_load(dplyr, stringr, tidyr, purrr, forcats, ggplot2,
               StatsBombR, soccermatics, SBpitch, ggsoccer,
               rlang, extrafont, ggupset)
loadfonts()
```


```{r}
comps <- FreeCompetitions()

glimpse(comps)
```

# Raw data

```{r}
messi_matches_raw <- comps %>% 
  filter(competition_id ==11) %>% 
  FreeMatches()


messi_data_raw <- StatsBombFreeEvents(MatchesDF = messi_matches_raw)

glimpse(messi_data_raw)
```

# Save raw

```{r}
saveRDS(messi_data_raw, file = here::here("data/messi_data_raw.RDS"))
messi_data_raw <- readRDS(file = here::here("data/messi_data_raw.RDS"))
```


# Clean all + add season labels

```{r}
messi_data_clean <- messi_data_raw %>% 
  allclean() %>%  ## cleanlocations, goalkeeper, shot, freezeframe, defensive
  left_join(comps %>% select(season_id, season_name), by = "season_id")
```

## Split games by season

```{r, eval=FALSE}
messi_split <- messi_data_clean %>% 
  group_split(season_id)

## check season ids
map(.x = messi_split, ~select(.x, season_id) %>% unique()) %>% bind_rows()


messi_2009_2010_df <- messi_split[[1]]
messi_2009_2010_df$season_id %>% unique()

messi_2010_2011_df <- messi_split[[2]]
messi_2010_2011_df$season_id %>% unique()

messi_2011_2012_df <- messi_split[[3]]
messi_2011_2012_df$season_id %>% unique()

messi_2004_2005_df <- messi_split[[4]]
messi_2004_2005_df$season_id %>% unique()

messi_2005_2006_df <- messi_split[[5]]
messi_2005_2006_df$season_id %>% unique()

messi_2006_2007_df <- messi_split[[6]]
messi_2006_2007_df$season_id %>% unique()

messi_2007_2008_df <- messi_split[[7]]
messi_2007_2008_df$season_id %>% unique()

messi_2008_2009_df <- messi_split[[8]]
messi_2008_2009_df$season_id %>% unique()
```

## Check

```{r}
glimpse(messi_data_clean)
```

```{r}
messi_data_clean %>% 
  select(type.name) %>% 
  unique()
```

## Barca player names

```{r}
messi_data_clean %>% 
  filter(team.name == "Barcelona") %>% 
  select(player.name, player.id) %>% unique()
```

Messi: 5503

```{r}
JoinPlayerNickName(messi_data_clean)
## i don't have a username or pwd... 
```

* manually clean the names...
* or find a nice list of players and join? 
* transfermarkt? no matter what list i find dont think it'll be a complete match
* use {fuzzyjoin} package? join even if ~n differences...

```{r}
messi_data_clean <- messi_data_clean %>% 
  ## player name
  mutate(player.name = case_when(
    player.name == "Oleguer Presas Renom" ~ "Oleguer",
    player.name == "Xavier Hernández Creus" ~ "Xavi",
    player.name == "Carles Puyol i Saforcada" ~ "Carles Puyol",
    player.name == "Anderson Luís de Souza" ~ "Deco",
    player.name == "Rafael Márquez Álvarez" ~ "Rafa Márquez",
    player.name == "Giovanni van Bronckhorst" ~ "Gio v.Bronckhorst",
    player.name == "Samuel Eto'o Fils" ~ "Samuel Eto'o",
    player.name == "Víctor Valdés Arribas" ~ "Víctor Valdés",
    player.name == "Juliano Haus Belletti" ~ "Juliano Belletti",
    player.name == "Ludovic Giuly" ~ "Ludovic Giuly",
    player.name == "Andrés Iniesta Luján" ~ "Andrés Iniesta",
    player.name == "Ronaldo de Assis Moreira" ~ "Ronaldinho",
    player.name == "Lionel Andrés Messi Cuccittini" ~ "Lionel Messi",
    player.name == "Fernando Navarro i Corbacho" ~ "Fernando Navarro",
    player.name == "Sylvio Mendes Campos Junior" ~ "Sylvinho",
    player.name == "Damià Abella Pérez" ~ "Damià",
    player.name == "Rubén Iván Martínez Andrade" ~ "Ronaldinho",
    player.name == "Ronaldo de Assis Moreira" ~ "Rubén",
    player.name == "Thiago Motta" ~ "Thiago Motta",
    player.name == "Mark van Bommel" ~ "Mark van Bommel",
    player.name == "Henrik Larsson" ~ "Henrik Larsson",
    player.name == "José Edmílson Gomes de Moraes" ~ "Edmílson",
    player.name == "Gabriel Francisco García de la Torre" ~ "Gabri",
    player.name == "Santiago Ezquerro Marín" ~ "Santi Ezquerro",
    player.name == "Maximiliano Gastón López" ~ "Maxi López",
    player.name == "Gianluca Zambrotta" ~ "Gianluca Zambrotta",
    player.name == "Eiður Smári Guðjohnsen" ~ "Eiður Guðjohnsen",
    player.name == "Lilian Thuram" ~ "Lilian Thuram",
    player.name == "Javier Pedro Saviola Fernández" ~ "Javier Saviola",
    player.name == "Gnégnéri Yaya Touré" ~ "Yaya Touré",
    player.name == "Bojan Krkíc Pérez" ~ "Bojan",
    player.name == "Eric-Sylvain Bilal Abidal" ~ "Eric Abidal",
    player.name == "Gabriel Alejandro Milito" ~ "Gabriel Milito",
    player.name == "Giovani dos Santos Ramírez" ~ "Giovani dos Santos",
    player.name == "Víctor Vázquez Solsona" ~ "Víctor Vázquez",
    player.name == "Thierry Henry" ~ "Thierry Henry",
    player.name == "José Manuel Pinto Colorado" ~ "José Manuel Pinto",
    player.name == "Daniel Alves da Silva" ~ "Dani Alves",
    player.name == "Sergio Busquets i Burgos" ~ "Sergio Busquets",
    player.name == "Seydou Kéita" ~ "Seydou Kéita",
    player.name == "José Martín Cáceres Silva" ~ "Martín Cáceres",
    player.name == "Gerard Piqué Bernabéu" ~ "Gerard Piqué",
    player.name == "Aliaksandr Hleb" ~ "Aliaksandr Hleb",
    player.name == "Pedro Eliezer Rodríguez Ledesma" ~ "Pedro",
    player.name == "Sergio Rodríguez García" ~ "Rodri",
    player.name == "Rafael Romero Serrano" ~ "Fali",
    player.name == "José Manuel Rueda Sampedro" ~ "José Manuel Rueda",
    player.name == "Zlatan Ibrahimovic" ~ "Zlatan Ibrahimovic",
    player.name == "Dmytro Chygrynskiy" ~ "Dmytro Chygrynskiy",
    player.name == "Maxwell Scherrer Cabelino Andrade" ~ "Maxwell",
    player.name == "Jeffren Isaac Suárez Bermúdez" ~ "Jeffren",
    player.name == "Víctor Sánchez Mata" ~ "Víctor Sánchez",
    player.name == "Thiago Alcântara do Nascimento" ~ "Thiago Alcântara",
    player.name == "David Villa Sánchez" ~ "David Villa",
    player.name == "Javier Alejandro Mascherano" ~ "Javier Mascherano",
    player.name == "Andreu Fontàs Prat" ~ "Andreu Fontàs",
    player.name == "Ibrahim Afellay" ~ "Ibrahim Afellay",
    player.name == "Manuel Agudo Durán" ~ "Nolito",
    player.name == "Marc Bartra Aregall" ~ "Marc Bartra",
    player.name == "Adriano Correia Claro" ~ "Adriano",
    player.name == "Martín Montoya Torralbo" ~ "Martín Montoya",
    player.name == "Jonathan dos Santos Ramírez" ~ "Jonathan dos Santos",
    player.name == "Francesc Fàbregas i Soler" ~ "Cesc Fàbregas",
    player.name == "Alexis Alejandro Sánchez Sánchez" ~ "Alexis Sánchez",
    player.name == "Juan Isaac Cuenca López" ~ "Isaac Cuenca",
    player.name == "Gerard Deulofeu Lázaro" ~ "Gerard Deulofeu",
    player.name == "Cristian Tello" ~ "Cristian Tello",
    player.name == "Sergi Roberto Carnicer" ~ "Sergi Roberto",
    player.name == "Marc Muniesa Martínez" ~ "Marc Muniesa",
    TRUE ~ player.name
  )) %>% 
  ## pass.recipient.name
  mutate(pass.recipient.name = case_when(
    pass.recipient.name == "Oleguer Presas Renom" ~ "Oleguer",
    pass.recipient.name == "Xavier Hernández Creus" ~ "Xavi",
    pass.recipient.name == "Carles Puyol i Saforcada" ~ "Carles Puyol",
    pass.recipient.name == "Anderson Luís de Souza" ~ "Deco",
    pass.recipient.name == "Rafael Márquez Álvarez" ~ "Rafa Márquez",
    pass.recipient.name == "Giovanni van Bronckhorst" ~ "Gio v.Bronckhorst",
    pass.recipient.name == "Samuel Eto'o Fils" ~ "Samuel Eto'o",
    pass.recipient.name == "Víctor Valdés Arribas" ~ "Víctor Valdés",
    pass.recipient.name == "Juliano Haus Belletti" ~ "Juliano Belletti",
    pass.recipient.name == "Ludovic Giuly" ~ "Ludovic Giuly",
    pass.recipient.name == "Andrés Iniesta Luján" ~ "Andrés Iniesta",
    pass.recipient.name == "Ronaldo de Assis Moreira" ~ "Ronaldinho",
    pass.recipient.name == "Lionel Andrés Messi Cuccittini" ~ "Lionel Messi",
    pass.recipient.name == "Fernando Navarro i Corbacho" ~ "Fernando Navarro",
    pass.recipient.name == "Sylvio Mendes Campos Junior" ~ "Sylvinho",
    pass.recipient.name == "Damià Abella Pérez" ~ "Damià",
    pass.recipient.name == "Rubén Iván Martínez Andrade" ~ "Ronaldinho",
    pass.recipient.name == "Ronaldo de Assis Moreira" ~ "Rubén",
    pass.recipient.name == "Thiago Motta" ~ "Thiago Motta",
    pass.recipient.name == "Mark van Bommel" ~ "Mark van Bommel",
    pass.recipient.name == "Henrik Larsson" ~ "Henrik Larsson",
    pass.recipient.name == "José Edmílson Gomes de Moraes" ~ "Edmílson",
    pass.recipient.name == "Gabriel Francisco García de la Torre" ~ "Gabri",
    pass.recipient.name == "Santiago Ezquerro Marín" ~ "Santi Ezquerro",
    pass.recipient.name == "Maximiliano Gastón López" ~ "Maxi López",
    pass.recipient.name == "Gianluca Zambrotta" ~ "Gianluca Zambrotta",
    pass.recipient.name == "Eiður Smári Guðjohnsen" ~ "Eiður Guðjohnsen",
    pass.recipient.name == "Lilian Thuram" ~ "Lilian Thuram",
    pass.recipient.name == "Javier Pedro Saviola Fernández" ~ "Javier Saviola",
    pass.recipient.name == "Gnégnéri Yaya Touré" ~ "Yaya Touré",
    pass.recipient.name == "Bojan Krkíc Pérez" ~ "Bojan",
    pass.recipient.name == "Eric-Sylvain Bilal Abidal" ~ "Eric Abidal",
    pass.recipient.name == "Gabriel Alejandro Milito" ~ "Gabriel Milito",
    pass.recipient.name == "Giovani dos Santos Ramírez" ~ "Giovani dos Santos",
    pass.recipient.name == "Víctor Vázquez Solsona" ~ "Víctor Vázquez",
    pass.recipient.name == "Thierry Henry" ~ "Thierry Henry",
    pass.recipient.name == "José Manuel Pinto Colorado" ~ "José Manuel Pinto",
    pass.recipient.name == "Daniel Alves da Silva" ~ "Dani Alves",
    pass.recipient.name == "Sergio Busquets i Burgos" ~ "Sergio Busquets",
    pass.recipient.name == "Seydou Kéita" ~ "Seydou Kéita",
    pass.recipient.name == "José Martín Cáceres Silva" ~ "Martín Cáceres",
    pass.recipient.name == "Gerard Piqué Bernabéu" ~ "Gerard Piqué",
    pass.recipient.name == "Aliaksandr Hleb" ~ "Aliaksandr Hleb",
    pass.recipient.name == "Pedro Eliezer Rodríguez Ledesma" ~ "Pedro",
    pass.recipient.name == "Sergio Rodríguez García" ~ "Rodri",
    pass.recipient.name == "Rafael Romero Serrano" ~ "Fali",
    pass.recipient.name == "José Manuel Rueda Sampedro" ~ "José Manuel Rueda",
    pass.recipient.name == "Zlatan Ibrahimovic" ~ "Zlatan Ibrahimovic",
    pass.recipient.name == "Dmytro Chygrynskiy" ~ "Dmytro Chygrynskiy",
    pass.recipient.name == "Maxwell Scherrer Cabelino Andrade" ~ "Maxwell",
    pass.recipient.name == "Jeffren Isaac Suárez Bermúdez" ~ "Jeffren",
    pass.recipient.name == "Víctor Sánchez Mata" ~ "Víctor Sánchez",
    pass.recipient.name == "Thiago Alcântara do Nascimento" ~ "Thiago Alcântara",
    pass.recipient.name == "David Villa Sánchez" ~ "David Villa",
    pass.recipient.name == "Javier Alejandro Mascherano" ~ "Javier Mascherano",
    pass.recipient.name == "Andreu Fontàs Prat" ~ "Andreu Fontàs",
    pass.recipient.name == "Ibrahim Afellay" ~ "Ibrahim Afellay",
    pass.recipient.name == "Manuel Agudo Durán" ~ "Nolito",
    pass.recipient.name == "Marc Bartra Aregall" ~ "Marc Bartra",
    pass.recipient.name == "Adriano Correia Claro" ~ "Adriano",
    pass.recipient.name == "Martín Montoya Torralbo" ~ "Martín Montoya",
    pass.recipient.name == "Jonathan dos Santos Ramírez" ~ "Jonathan dos Santos",
    pass.recipient.name == "Francesc Fàbregas i Soler" ~ "Cesc Fàbregas",
    pass.recipient.name == "Alexis Alejandro Sánchez Sánchez" ~ "Alexis Sánchez",
    pass.recipient.name == "Juan Isaac Cuenca López" ~ "Isaac Cuenca",
    pass.recipient.name == "Gerard Deulofeu Lázaro" ~ "Gerard Deulofeu",
    pass.recipient.name == "Cristian Tello" ~ "Cristian Tello",
    pass.recipient.name == "Sergi Roberto Carnicer" ~ "Sergi Roberto",
    pass.recipient.name == "Marc Muniesa Martínez" ~ "Marc Muniesa",
    TRUE ~ pass.recipient.name
  ))
```


```{r}
messi_data_clean %>% 
  filter(team.name == "Barcelona") %>% 
  select(player.name) %>% 
  unique()
```


```{r}
messi_2007_2008_df %>% 
  filter(team.name == "Barcelona") %>% 
  select(player.name) %>% 
  unique()
```

# Save clean

```{r}
saveRDS(messi_data_clean, file = here::here("data/messi_data_clean.RDS"))
messi_data_clean <- readRDS(file = here::here("data/messi_data_clean.RDS"))
```


# Data: Completed Pass Received - OPEN PLAY (games where Messi played)

## ALL

```{r}
pass_received_all <- messi_data_clean %>% 
  mutate(pass.outcome.name = fct_explicit_na(pass.outcome.name, "Complete")) %>%
  filter(type.name == "Pass",
         team.name == "Barcelona",
         pass.outcome.name == "Complete",
         !play_pattern.name %in% c("From Corner", "From Free Kick",
                                   "From Throw In")) %>% 
  select(player.name, pass.recipient.name, 
         season_id, season_name,
         position.name, position.id,
         location.x, location.y,
         pass.end_location.x, pass.end_location.y,
         contains("pass")) %>% 
  group_by(season_name) %>% 
  add_count(player.name, pass.recipient.name, name = "pass_num") %>% 
  ungroup() %>% 
  mutate(player.name = glue::glue("{player.name}: {pass_num}")) %>% 
  mutate(pass_duo = map2(player.name, pass.recipient.name, ~c(.x, .y))) %>% 
  select(player.name, pass.recipient.name, pass_num, 
         season_name, pass_duo)
```

## * ALL box

```{r}
pass_received_all_box <- messi_data_clean %>% 
  mutate(pass.outcome.name = fct_explicit_na(pass.outcome.name, "Complete")) %>%
  filter(type.name == "Pass",
         team.name == "Barcelona",
         pass.outcome.name == "Complete",
         !play_pattern.name %in% c("From Corner", "From Free Kick",
                                   "From Throw In"),
         pass.end_location.x >= 102 & pass.end_location.y <= 62 &
           pass.end_location.y >= 18) %>% 
  select(player.name, pass.recipient.name, 
         season_id, season_name,
         position.name, position.id,
         location.x, location.y,
         pass.end_location.x, pass.end_location.y,
         contains("pass")) %>% 
  group_by(season_name) %>% 
  add_count(player.name, pass.recipient.name, name = "pass_num") %>% 
  ungroup() %>% 
  mutate(player.name = glue::glue("{player.name}: {pass_num}")) %>% 
  mutate(pass_duo = map2(player.name, pass.recipient.name, ~c(.x, .y))) %>% 
  select(player.name, pass.recipient.name, pass_num, 
         season_name, pass_duo)
```

## ALL Messi Passer

```{r}
messi_passer_all <- messi_data_clean %>% 
  mutate(pass.outcome.name = fct_explicit_na(pass.outcome.name, "Complete")) %>%
  filter(type.name == "Pass",
         team.name == "Barcelona",
         pass.outcome.name == "Complete",
         !play_pattern.name %in% c("From Corner", "From Free Kick",
                                   "From Throw In")) %>% 
  select(player.name, pass.recipient.name, 
         season_id, season_name,
         position.name, position.id,
         location.x, location.y,
         pass.end_location.x, pass.end_location.y,
         contains("pass")) %>% 
  group_by(season_name) %>% 
  add_count(player.name, pass.recipient.name, name = "pass_num") %>% 
  ungroup() %>% 
  filter(player.name == "Lionel Messi") %>% 
  mutate(player.name = glue::glue("{player.name}: {pass_num}")) %>% 
  mutate(pass_duo = map2(player.name, pass.recipient.name, ~c(.x, .y))) %>% 
  select(player.name, pass.recipient.name, pass_num, 
         season_name, pass_duo)
```


## total - Messi

```{r}
messi_pass_received_total <- messi_data_clean %>% 
  mutate(pass.outcome.name = fct_explicit_na(pass.outcome.name, "Complete")) %>%
  filter(type.name == "Pass",
         pass.outcome.name == "Complete",
         pass.recipient.id == 5503,
         !play_pattern.name %in% c("From Corner", "From Free Kick",
                                   "From Throw In")) %>% 
  select(player.name, pass.recipient.name, 
         season_id, season_name,
         position.name, position.id,
         location.x, location.y,
         pass.end_location.x, pass.end_location.y,
         contains("pass")) %>% 
  group_by(season_name) %>% 
  add_count(player.name, pass.recipient.name, name = "pass_num") %>% 
  ungroup() %>% 
  mutate(player.name = case_when(
    player.name != "Lionel Messi" ~ 
      glue::glue("{player.name}: {pass_num}")),
    pass.recipient.name = "Lionel Messi") %>% 
  mutate(pass_duo = map2(player.name, pass.recipient.name, ~c(.x, .y))) %>% 
  select(player.name, pass_num, 
         season_name, pass_duo) #%>% 
  #distinct(player.name, season_name, .keep_all = TRUE)
```


## box - Messi

```{r}
messi_pass_received_box <- messi_data_clean %>% 
  mutate(pass.outcome.name = fct_explicit_na(pass.outcome.name, "Complete")) %>%
  filter(type.name == "Pass",
         pass.outcome.name == "Complete",
         pass.recipient.id == 5503,
         !play_pattern.name %in% c("From Corner", "From Free Kick",
                                   "From Throw In"),
         pass.end_location.x >= 102 & pass.end_location.y <= 62 &
           pass.end_location.y >= 18) %>% 
  select(player.name, pass.recipient.name, 
         season_id, season_name,
         position.name, position.id,
         location.x, location.y,
         pass.end_location.x, pass.end_location.y,
         contains("pass")) %>% 
  group_by(season_name) %>% 
  add_count(player.name, pass.recipient.name, name = "pass_num") %>% 
  ungroup() %>% 
  mutate(player.name = case_when(
    player.name != "Lionel Messi" ~ 
      glue::glue("{player.name}: {pass_num}")),
    pass.recipient.name = "Lionel Messi") %>% 
  mutate(pass_duo = map2(player.name, pass.recipient.name, ~c(.x, .y)))
```

## box - passer Messi

```{r}
messi_passer_box <- messi_data_clean %>% 
  mutate(pass.outcome.name = fct_explicit_na(pass.outcome.name, "Complete")) %>%
  filter(type.name == "Pass",
         team.name == "Barcelona",
         pass.outcome.name == "Complete",
         !play_pattern.name %in% c("From Corner", "From Free Kick",
                                   "From Throw In"),
         pass.end_location.x >= 102 & pass.end_location.y <= 62 &
           pass.end_location.y >= 18) %>% 
  select(player.name, pass.recipient.name, 
         season_id, season_name,
         position.name, position.id,
         location.x, location.y,
         pass.end_location.x, pass.end_location.y,
         contains("pass")) %>% 
  group_by(season_name) %>% 
  add_count(player.name, pass.recipient.name, name = "pass_num") %>% 
  ungroup() %>% 
  filter(player.name == "Lionel Messi") %>% 
  mutate(player.name = glue::glue("{player.name}: {pass_num}")) %>% 
  mutate(pass_duo = map2(player.name, pass.recipient.name, ~c(.x, .y))) %>% 
  select(player.name, pass.recipient.name, pass_num, 
         season_name, pass_duo)
```


# Upset Plots

* CAVEAT: Data only for games where Messi played!
* Injury, benched, rested, etc.
* In certain seasons, Messi was injured a lot! So numbers across seasons may not transfer well in interpretation...
* x-axis label ranked by number of passes (received or given)

```{r eval=FALSE}
messi_data_clean %>% 
  filter(team.name == "Barcelona") %>% 
  filter(!is.na(pass.shot_assist) | !is.na(pass.goal_assist)) %>% 
  View()

```

from Transfermarkt:
2004/2005: 7/38 games
2005/2006: 17/38 games
2006/2007: 26/38 games
2007/2008: 28/38 games
2008/2009: 31/38 games
2009/2010: 35/38 games
2010/2011: 33/38 games
2011/2012: 37/38 games

```{r}
messi_data_clean %>% 
  select(season_id, season_name) %>% 
  unique()

messi_data_clean %>% 
  group_by(season_id, season_name) %>% 
  select(match_id) %>% unique() %>% count() %>% 
  ungroup() %>% 
  mutate(sum = sum(n)) # total matches in dataset
```



```{r}
messi_passduo <- messi_pass_received %>% 
  select(player.name, pass_duo, season_name, pass_num) %>% 
  filter(season_name == "2011/2012") %>% 
  distinct(player.name, .keep_all = TRUE) %>% 
  #arrange(desc(pass_num)) %>% 
  ggplot(aes(x = reorder(pass_duo, pass_num), y = pass_num)) +
  geom_col(fill = "#a70042") + 
  geom_text(aes(label = pass_num),
            nudge_y = 5) +
  scale_x_upset(n_intersections = 10,
                order_by = "freq",
                expand = c(0.01, 0.01)) +
  scale_y_continuous(expand = c(0.05, 0)) +
  labs(title = "Passes to Messi (2011-2012 Season)",
       subtitle = str_wrap("Xavi passed to Messi more than double the amount of times of the 2nd highest passer, Zambrotta", width = 70),
       caption = "Source: StatsBomb",
       x = NULL, y = "Number of Passes") +
  theme_combmatrix(
    text = element_text(family = "Roboto Condensed", color = "#a70042"),
    axis.text.y = element_text(family = "Roboto Condensed", color = "#a70042"),
    panel.background = element_rect(fill = "#004c99"),
    combmatrix.panel.point.color.fill = "#004c99",
    combmatrix.panel.line.color = "#004c99",
    panel.grid.major.x = element_blank(),
    axis.ticks = element_blank())

messi_passduo
```


## all

'Name: Number' == PASSER! 'No Number' == Pass Receiver

```{r, fig.height=6, fig.width=8}
all_pass_nested_total <- pass_received_all %>% 
  group_by(season_name) %>% 
  nest() %>%
  mutate(plot = map2(
    data, season_name,
    ~ ggplot(data = .x, aes(x = pass_duo)) +
      geom_bar(fill = "#a70042") + 
      scale_x_upset(n_intersections = 10,
                    expand = c(0.01, 0.01)) +
      scale_y_continuous(expand = c(0.04, 0.04)) +
      labs(title = glue::glue("Total Passes Between All Players ({.y})"),
           subtitle = "'Name: Number' = Passer, 'No Number' = Pass Receiver",
           caption = "Source: StatsBomb",
           x = NULL, y = "Number of Passes") +
      theme_combmatrix(
        text = element_text(family = "Roboto Condensed", 
                            color = "#004c99"),
        plot.title = element_text(family = "Roboto Condensed", size = 20,
                                  color = "#a70042"),
        plot.subtitle = element_text(family = "Roboto Condensed", size = 16,
                                     color = "#004c99"),
        axis.title = element_text(family = "Roboto Condensed", size = 14,
                                  color = "#004c99"), 
        axis.text.x = element_text(family = "Roboto Condensed", size = 12,
                                   color = "#004c99"),
        axis.text.y = element_text(family = "Roboto Condensed", size = 12,
                                   color = "#004c99"),
        panel.background = element_rect(fill = "white"),
        combmatrix.panel.point.size = 4,
        combmatrix.panel.point.color.fill = "#a70042",
        combmatrix.panel.line.color = "#a70042",
        panel.grid = element_line(color = "black"),
        panel.grid.major.x = element_blank(),
        axis.ticks = element_blank())))

all_pass_nested_total$plot[[8]] +
  scale_y_continuous(labels = seq(0, 230, by = 50),
                     breaks = seq(0, 230, by = 50),
                     limits = c(0, 230))
```

### 2004-2005

```{r, fig.height=6, fig.width=8}
all_pass_nested_total$plot[[1]] +
  scale_y_continuous(labels = seq(0, 50, by = 10),
                     breaks = seq(0, 50, by = 10),
                     limits = c(0, 50))
```



### 2005-2006

```{r, fig.height=6, fig.width=8}
all_pass_nested_total$plot[[2]] +
  scale_y_continuous(labels = seq(0, 90, by = 20),
                     breaks = seq(0, 90, by = 20),
                     limits = c(0, 90))
```

* Ronaldinho + Sylvinho partnership on the left wing + left half-space
* Rafa Marquez and Puyol's central D partnership
* Deco & Ronaldinho play-making duo

### 2006-2007

```{r}
all_pass_nested_total$plot[[3]] +
  scale_y_continuous(labels = seq(0, 150, by = 20),
                     breaks = seq(0, 150, by = 20),
                     limits = c(0, 150))
```


### 2007-2008

```{r}
all_pass_nested_total$plot[[4]] +
  scale_y_continuous(labels = seq(0, 180, by = 30),
                     breaks = seq(0, 180, by = 30),
                     limits = c(0, 180))
```


### 2008-2009

```{r}
all_pass_nested_total$plot[[5]] +
  scale_y_continuous(labels = seq(0, 250, by = 50),
                     breaks = seq(0, 250, by = 50),
                     limits = c(0, 250))
```

### 2009-2010

```{r, fig.height=12}
all_pass_nested_total$plot[[6]] +
  scale_y_continuous(labels = seq(0, 250, by = 50),
                     breaks = seq(0, 250, by = 50),
                     limits = c(0, 250))
```

### 2010-2011

```{r}
all_pass_nested_total$plot[[7]] +
  scale_y_continuous(labels = seq(0, 260, by = 50),
                     breaks = seq(0, 260, by = 50),
                     limits = c(0, 260))
```

### 2011-2012

```{r}
all_pass_nested_total$plot[[8]] +
  scale_y_continuous(labels = seq(0, 260, by = 50),
                     breaks = seq(0, 260, by = 50),
                     limits = c(0, 240))
```



## all - box

* Messi goes from Passer to Receiver!

```{r, fig.height=6, fig.width=8}
all_pass_nested_box <- pass_received_all_box %>% 
  group_by(season_name) %>% 
  nest() %>%
  mutate(plot = map2(
    data, season_name,
    ~ ggplot(data = .x, aes(x = pass_duo)) +
      geom_bar(fill = "#a70042") + 
      scale_x_upset(n_intersections = 10,
                    expand = c(0.01, 0.01)) +
      scale_y_continuous(expand = c(0.04, 0.04)) +
      labs(title = glue::glue("
                              Total Completed Passes Into The Box 
                              Between All Players ({.y})"),
           subtitle = "'Name: Number' = Passer, 'No Number' = Pass Receiver",
           caption = "Source: StatsBomb",
           x = NULL, y = "Number of Passes") +
      theme_combmatrix(
        text = element_text(family = "Roboto Condensed", 
                            color = "#004c99"),
        plot.title = element_text(family = "Roboto Condensed", size = 20,
                                  color = "#a70042"),
        plot.subtitle = element_text(family = "Roboto Condensed", size = 16,
                                     color = "#004c99"),
        axis.title = element_text(family = "Roboto Condensed", size = 14,
                                  color = "#004c99"), 
        axis.text.x = element_text(family = "Roboto Condensed", size = 12,
                                   color = "#004c99"),
        axis.text.y = element_text(family = "Roboto Condensed", size = 12,
                                   color = "#004c99"),
        panel.background = element_rect(fill = "white"),
        combmatrix.panel.point.size = 4,
        combmatrix.panel.point.color.fill = "#a70042",
        combmatrix.panel.line.color = "#a70042",
        panel.grid = element_line(color = "black"),
        panel.grid.major.x = element_blank(),
        axis.ticks = element_blank())))

all_pass_nested_box$plot[[8]] +
  scale_y_continuous(labels = seq(0, 15, by = 5),
                     breaks = seq(0, 15, by = 5),
                     limits = c(0, 15))
```

### 2004-2005

```{r}
all_pass_nested_box$plot[[1]] +
  scale_y_continuous(labels = seq(0, 6, by = 1),
                     breaks = seq(0, 6, by = 1),
                     limits = c(0, 6))
```



### 2005-2006

```{r}
all_pass_nested_box$plot[[2]] +
  scale_y_continuous(labels = seq(0, 8, by = 1),
                     breaks = seq(0, 8, by = 1),
                     limits = c(0, 8))
```

* Deco and Ronaldinho's passing not seen in the box (compare to total passing chart 2005/2006)
* Deco playmaking from deeper and letting Ronaldinho "dance" and then give the final ball to Messi, Eto'o, Henrik Larsson

### 2006-2007

```{r}
all_pass_nested_box$plot[[3]] +
  scale_y_continuous(labels = seq(0, 12, by = 2),
                     breaks = seq(0, 12, by = 2),
                     limits = c(0, 12))
```


### 2007-2008

```{r}
all_pass_nested_box$plot[[4]] +
  scale_y_continuous(labels = seq(0, 10, by = 2),
                     breaks = seq(0, 10, by = 2),
                     limits = c(0, 10))
```

* Messi starts his dominance of Barca's attacking play into the box (both receiving AND passing)
* Henry received the ball the most 

### 2008-2009

* Messi feeding Henry and Eto'o

```{r}
all_pass_nested_box$plot[[5]] +
  scale_y_continuous(labels = seq(0, 20, by = 5),
                     breaks = seq(0, 20, by = 5),
                     limits = c(0, 20))
```

* Messi the main supplier to the fellow strikers Henry & Eto'o (Messi - Eto'o - Henry???)
* Messi - Henry: 18, Messi - Eto'o: 17, Messi - Iniesta: 13

### 2009-2010

```{r}
all_pass_nested_box$plot[[6]] +
  scale_y_continuous(labels = seq(0, 20, by = 5),
                     breaks = seq(0, 20, by = 5),
                     limits = c(0, 20)) +
  theme(plot.caption = element_text(glue::glue("
                             Messi: 14 (7 to Dani Alves & 7 to Henry)
                             Source: StatsBomb")))
```

### 2010-2011

```{r}
all_pass_nested_box$plot[[7]] +
  scale_y_continuous(labels = seq(0, 28, by = 5),
                     breaks = seq(0, 28, by = 5),
                     limits = c(0, 28))
```

* Messi on the receiving end of passes in the box along with David Villa

### * 2011-2012

```{r}
pass_received_all_box %>% 
  filter(season_name == "2011/2012") %>% 
  distinct(player.name, pass.recipient.name, .keep_all = TRUE) %>% View()
```

What should the table include?
* Total num "Passes"
* SUM Pass type
* SUM pass height name 
* SUM pass footedness (left, right,... other?)

```{r}
pass_received_all_box %>% 
  filter(season_name == "2011/2012") %>% 
  distinct(player.name, pass.recipient.name, .keep_all = TRUE) %>% 
  select(player.name, pass_num) %>% 
  mutate(player.name = player.name %>% str_replace_all(., "\\: [0-9]*", "")) %>% 
  group_by(player.name) %>% 
  mutate(pass_sum = sum(pass_num)) %>% 
  ungroup() %>% 
  distinct(player.name, pass_sum) %>% 
  arrange(desc(pass_sum)) %>% 
  rename(Player = player.name, 
         Passes = pass_sum)
```

https://cran.r-project.org/web/packages/gridExtra/vignettes/tableGrob.html

* Messi gave 67 completed passes into the box!! almost more than double next best Dani Alves (34)


```{r}
all_pass_nested_box$plot[[8]] +
  scale_y_continuous(labels = seq(0, 15, by = 5),
                     breaks = seq(0, 15, by = 5),
                     limits = c(0, 15))
```

* Dani Alves & Messi partnership in full flight

## total - Messi

```{r, fig.height=6, fig.width=8}
messi_pass_nested_total <- messi_pass_received_total %>% 
  group_by(season_name) %>% 
  nest() %>%
  mutate(plot = map2(
    data, season_name,
    ~ ggplot(data = .x, aes(x = pass_duo)) +
      geom_bar(fill = "#ffee00") + 
      scale_x_upset(n_intersections = 10,
                    expand = c(0.01, 0.01)) +
      scale_y_continuous(expand = c(0.04, 0.04)) +
      labs(title = glue::glue("Total Passes to Messi ({.y})"),
           subtitle = "",
           caption = "Source: StatsBomb",
           x = NULL, y = "Number of Passes") +
      theme_combmatrix(
        text = element_text(family = "Roboto Condensed", 
                            color = "#a70042"),
        plot.title = element_text(family = "Roboto Condensed", size = 20,
                                  color = "#a70042"),
        plot.subtitle = element_text(family = "Roboto Condensed", size = 16,
                                     color = "#a70042"),
        axis.title = element_text(family = "Roboto Condensed", size = 14,
                                  color = "#a70042"), 
        axis.text.x = element_text(family = "Roboto Condensed", size = 12,
                                   color = "#a70042"),
        axis.text.y = element_text(family = "Roboto Condensed", size = 12,
                                   color = "#a70042"),
        panel.background = element_rect(fill = "#004c99"),
        combmatrix.panel.point.size = 4,
        combmatrix.panel.point.color.fill = "#ffee00",
        combmatrix.panel.line.color = "#ffee00",
        panel.grid.major.x = element_blank(),
        axis.ticks = element_blank())))

messi_pass_nested_total$plot[[8]] +
  scale_y_continuous(labels = seq(0, 260, by = 50),
                     breaks = seq(0, 260, by = 50),
                     limits = c(0, 240))
```



### 2004-2005

```{r}
messi_pass_nested_total$plot[[1]] +
  scale_y_continuous(labels = seq(0, 6, by = 2),
                     breaks = seq(0, 6, by = 2),
                     limits = c(0, 6))
```



### 2005-2006

```{r}
messi_pass_nested_total$plot[[2]] +
  scale_y_continuous(labels = seq(0, 33, by = 5),
                     breaks = seq(0, 33, by = 5),
                     limits = c(0, 33))
```

### 2006-2007

```{r}
messi_pass_nested_total$plot[[3]] +
  scale_y_continuous(labels = seq(0, 130, by = 20),
                     breaks = seq(0, 130, by = 20),
                     limits = c(0, 130))
```


### 2007-2008

```{r}
messi_pass_nested_total$plot[[4]] +
  scale_y_continuous(labels = seq(0, 165, by = 20),
                     breaks = seq(0, 165, by = 20),
                     limits = c(0, 165))
```

* Xavi has more than double the amount of completed passes to Messi compared to Zambrotta!!

### 2008-2009

```{r}
messi_pass_nested_total$plot[[5]] +
  scale_y_continuous(labels = seq(0, 200, by = 20),
                     breaks = seq(0, 200, by = 20),
                     limits = c(0, 200))
```

* Dani Alves + Xavi

### 2009-2010

```{r}
messi_pass_nested_total$plot[[6]] +
  scale_y_continuous(labels = seq(0, 130, by = 20),
                     breaks = seq(0, 130, by = 20),
                     limits = c(0, 130))
```

### 2010-2011

```{r}
messi_pass_nested_total$plot[[7]] +
  scale_y_continuous(labels = seq(0, 260, by = 50),
                     breaks = seq(0, 260, by = 50),
                     limits = c(0, 260))
```

### 2011-2012

```{r}
messi_pass_nested_total$plot[[8]] +
  scale_y_continuous(labels = seq(0, 260, by = 50),
                     breaks = seq(0, 260, by = 50),
                     limits = c(0, 240))
```

## box - Messi

```{r, fig.height=6, fig.width=8}
messi_pass_nested_box <- messi_pass_received_box %>% 
  group_by(season_name) %>% 
  nest() %>%
  mutate(plot = map2(
    data, season_name,
    ~ ggplot(data = .x, aes(x = pass_duo)) +
      geom_bar(fill = "#a70042") + 
      scale_x_upset(n_intersections = 10,
                    expand = c(0.01, 0.01)) +
      scale_y_continuous(expand = c(0.04, 0.04)) +
      labs(title = glue::glue("Passes to Messi in the Box ({.y})"),
           subtitle = "",
           caption = "Source: StatsBomb",
           x = NULL, y = "Number of Passes") +
      theme_combmatrix(
        text = element_text(family = "Roboto Condensed", 
                            color = "#004c99"),
        plot.title = element_text(family = "Roboto Condensed", size = 20,
                                  color = "#a70042"),
        plot.subtitle = element_text(family = "Roboto Condensed", size = 16,
                                     color = "#004c99"),
        axis.title = element_text(family = "Roboto Condensed", size = 14,
                                  color = "#004c99"), 
        axis.text.x = element_text(family = "Roboto Condensed", size = 12,
                                   color = "#004c99"),
        axis.text.y = element_text(family = "Roboto Condensed", size = 12,
                                   color = "#004c99"),
        panel.background = element_rect(fill = "white"),
        combmatrix.panel.point.size = 4,
        combmatrix.panel.point.color.fill = "#a70042",
        combmatrix.panel.line.color = "#a70042",
        panel.grid = element_line(color = "black"),
        panel.grid.major.x = element_blank(),
        axis.ticks = element_blank())))

messi_pass_nested_box$plot[[8]] +
  scale_y_continuous(labels = seq(0, 14, by = 2),
                     breaks = seq(0, 14, by = 2),
                     limits = c(0, 14))
```



### 2004-2005

```{r}
messi_pass_nested_box$plot[[1]] +
  scale_y_continuous(labels = seq(0, 4, by = 2),
                     breaks = seq(0, 4, by = 2),
                     limits = c(0, 4))
```



### 2005-2006

```{r}
messi_pass_nested_box$plot[[2]] +
  scale_y_continuous(labels = seq(0, 6, by = 2),
                     breaks = seq(0, 6, by = 2),
                     limits = c(0, 6))
```


### 2006-2007

```{r}
messi_pass_nested_box$plot[[3]] +
  scale_y_continuous(labels = seq(0, 6, by = 2),
                     breaks = seq(0, 6, by = 2),
                     limits = c(0, 6))
```


### 2007-2008

```{r}
messi_pass_nested_box$plot[[4]] +
  scale_y_continuous(labels = seq(0, 8, by = 2),
                     breaks = seq(0, 8, by = 2),
                     limits = c(0, 8))
```


### 2008-2009

```{r}
messi_pass_nested_box$plot[[5]] +
  scale_y_continuous(labels = seq(0, 18, by = 2),
                     breaks = seq(0, 18, by = 2),
                     limits = c(0, 18))
```

### 2009-2010

```{r, fig.height=6, fig.width=8}
messi_pass_nested_box$plot[[6]] +
  scale_y_continuous(labels = seq(0, 20, by = 2),
                     breaks = seq(0, 20, by = 2),
                     limits = c(0, 20))
```

### 2010-2011

```{r, fig.height=6, fig.width=8}
messi_pass_nested_box$plot[[7]] +
  scale_y_continuous(labels = seq(0, 25, by = 5),
                     breaks = seq(0, 25, by = 5),
                     limits = c(0, 25))
```

### * 2011-2012

```{r}
messi_pass_nested_box$plot[[8]] +
  scale_y_continuous(labels = seq(0, 14, by = 2),
                     breaks = seq(0, 14, by = 2),
                     limits = c(0, 14))
```

### Dani Alves to Messi: by shot-assist

```{r}
ggplot(messi_alves_1112) +
  annotate_pitch(dimensions = pitch_statsbomb) +
  geom_segment(aes(x = location.x, y = location.y,                               
                   xend = pass.end_location.x, yend = pass.end_location.y),      
               lineend = "round", size = 0.6,
               arrow = arrow(length = unit(0.08, "inches"))) + 
  theme_pitch() +
  direction_label(x_label = 60) +
  labs(title = "Completed Box Passes to Messi (2011/2012)", 
       subtitle = glue::glue("
                             {messi_alves_1112$player.name}: {messi_alves_1112$pass_num}")) +  
  theme(text = element_text(family = "Roboto Condensed"))
```


# Shot/Goal Assist


```{r}
messi_data_clean %>% 
  filter(team.name == "Barcelona") %>% 
  filter(!is.na(pass.shot_assist) | !is.na(pass.goal_assist)) %>% 
  View()
```

## Shot Assist

```{r}
messi_all_shot_assist <- messi_data_clean %>% 
  mutate(pass.outcome.name = fct_explicit_na(pass.outcome.name, "Complete")) %>%
  filter(team.name == "Barcelona",
         !is.na(pass.shot_assist),
         !play_pattern.name %in% c("From Corner", "From Free Kick",
                                   "From Throw In")) %>% 
  select(player.name, pass.recipient.name, 
         season_id, season_name,
         position.name, position.id,
         location.x, location.y,
         pass.end_location.x, pass.end_location.y,
         contains("pass")) %>% 
  group_by(season_name) %>% 
  add_count(player.name, pass.recipient.name, name = "pass_num") %>% 
  ungroup() %>% 
  mutate(player.name = glue::glue("{player.name}: {pass_num}")) %>% 
  mutate(pass_duo = map2(player.name, pass.recipient.name, ~c(.x, .y))) %>% 
  select(player.name, pass.recipient.name, pass_num, 
         season_name, pass_duo)

messi_all_shot_assist %>% 
  distinct(player.name, pass.recipient.name, .keep_all = TRUE) %>% 
  arrange(desc(pass_num))
```


```{r}
messi_nested_all_shot_assist <- messi_all_shot_assist %>% 
  group_by(season_name) %>% 
  nest() %>%
  mutate(plot = map2(
    data, season_name,
    ~ ggplot(data = .x, aes(x = pass_duo)) +
      geom_bar(fill = "#a70042") + 
      scale_x_upset(n_intersections = 10,
                    expand = c(0.01, 0.01)) +
      scale_y_continuous(expand = c(0.04, 0.04)) +
      labs(title = glue::glue("Shot Assists ({.y})"),
           subtitle = "'Name: Number' = Passer, 'No Number' = Pass Receiver",
           caption = "Source: StatsBomb",
           x = NULL, y = "Number of Passes") +
      theme_combmatrix(
        text = element_text(family = "Roboto Condensed", 
                            color = "#004c99"),
        plot.title = element_text(family = "Roboto Condensed", size = 20,
                                  color = "#a70042"),
        plot.subtitle = element_text(family = "Roboto Condensed", size = 16,
                                     color = "#004c99"),
        axis.title = element_text(family = "Roboto Condensed", size = 14,
                                  color = "#004c99"), 
        axis.text.x = element_text(family = "Roboto Condensed", size = 12,
                                   color = "#004c99"),
        axis.text.y = element_text(family = "Roboto Condensed", size = 12,
                                   color = "#004c99"),
        panel.background = element_rect(fill = "white"),
        combmatrix.panel.point.size = 4,
        combmatrix.panel.point.color.fill = "#a70042",
        combmatrix.panel.line.color = "#a70042",
        panel.grid = element_line(color = "black"),
        panel.grid.major.x = element_blank(),
        axis.ticks = element_blank())))

messi_nested_all_shot_assist$plot[[8]] +
  scale_y_continuous(labels = seq(0, 12, by = 2),
                     breaks = seq(0, 12, by = 2),
                     limits = c(0, 12))
```


### 2004-2005

```{r}
messi_nested_all_shot_assist$plot[[1]] +
  scale_y_continuous(labels = seq(0, 6, by = 2),
                     breaks = seq(0, 6, by = 2),
                     limits = c(0, 6))
```



### 2005-2006

```{r}
messi_nested_all_shot_assist$plot[[2]] +
  scale_y_continuous(labels = seq(0, 6, by = 2),
                     breaks = seq(0, 6, by = 2),
                     limits = c(0, 6))
```



### 2006-2007

```{r}
messi_nested_all_shot_assist$plot[[3]] +
  scale_y_continuous(labels = seq(0, 12, by = 2),
                     breaks = seq(0, 12, by = 2),
                     limits = c(0, 12))
```


### 2007-2008

```{r}
messi_nested_all_shot_assist$plot[[4]] +
  scale_y_continuous(labels = seq(0, 6, by = 2),
                     breaks = seq(0, 6, by = 2),
                     limits = c(0, 6))
```


### 2008-2009

```{r}
messi_nested_all_shot_assist$plot[[5]] +
  scale_y_continuous(labels = seq(0, 12, by = 2),
                     breaks = seq(0, 12, by = 2),
                     limits = c(0, 12))
```

### 2009-2010

```{r, fig.height=6, fig.width=8}
messi_nested_all_shot_assist$plot[[6]] +
  scale_y_continuous(labels = seq(0, 14, by = 2),
                     breaks = seq(0, 14, by = 2),
                     limits = c(0, 14))
```

### 2010-2011

```{r, fig.height=6, fig.width=8}
messi_nested_all_shot_assist$plot[[7]] +
  scale_y_continuous(labels = seq(0, 18, by = 2),
                     breaks = seq(0, 18, by = 2),
                     limits = c(0, 18))
```

### * 2011-2012

```{r}
messi_nested_all_shot_assist$plot[[8]] +
  scale_y_continuous(labels = seq(0, 12, by = 2),
                     breaks = seq(0, 12, by = 2),
                     limits = c(0, 12))
```







## Goal Assist

```{r}
messi_all_goal_assist <- messi_data_clean %>% 
  mutate(pass.outcome.name = fct_explicit_na(pass.outcome.name, "Complete")) %>%
  filter(team.name == "Barcelona",
         !is.na(pass.goal_assist),
         !play_pattern.name %in% c("From Corner", "From Free Kick",
                                   "From Throw In")) %>% 
  select(player.name, pass.recipient.name, 
         season_id, season_name,
         position.name, position.id,
         location.x, location.y,
         pass.end_location.x, pass.end_location.y,
         contains("pass")) %>% 
  group_by(season_name) %>% 
  add_count(player.name, pass.recipient.name, name = "pass_num") %>% 
  ungroup() %>% 
  mutate(player.name = glue::glue("{player.name}: {pass_num}")) %>% 
  mutate(pass_duo = map2(player.name, pass.recipient.name, ~c(.x, .y))) %>% 
  select(player.name, pass.recipient.name, pass_num, 
         season_name, pass_duo) 

messi_all_goal_assist %>% 
  distinct(player.name, pass.recipient.name, .keep_all = TRUE) %>% 
  arrange(desc(pass_num))
```



```{r}
messi_nested_all_goal_assist <- messi_all_goal_assist %>% 
  group_by(season_name) %>% 
  nest() %>%
  mutate(plot = map2(
    data, season_name,
    ~ ggplot(data = .x, aes(x = pass_duo)) +
      geom_bar(fill = "#a70042") + 
      scale_x_upset(n_intersections = 10,
                    expand = c(0.01, 0.01)) +
      scale_y_continuous(expand = c(0.04, 0.04)) +
      labs(title = glue::glue("Goal Assists ({.y})"),
           subtitle = "'Name: Number' = Passer, 'No Number' = Pass Receiver",
           caption = "Source: StatsBomb",
           x = NULL, y = "Number of Passes") +
      theme_combmatrix(
        text = element_text(family = "Roboto Condensed", 
                            color = "#004c99"),
        plot.title = element_text(family = "Roboto Condensed", size = 20,
                                  color = "#a70042"),
        plot.subtitle = element_text(family = "Roboto Condensed", size = 16,
                                     color = "#004c99"),
        axis.title = element_text(family = "Roboto Condensed", size = 14,
                                  color = "#004c99"), 
        axis.text.x = element_text(family = "Roboto Condensed", size = 12,
                                   color = "#004c99"),
        axis.text.y = element_text(family = "Roboto Condensed", size = 12,
                                   color = "#004c99"),
        panel.background = element_rect(fill = "white"),
        combmatrix.panel.point.size = 4,
        combmatrix.panel.point.color.fill = "#a70042",
        combmatrix.panel.line.color = "#a70042",
        panel.grid = element_line(color = "black"),
        panel.grid.major.x = element_blank(),
        axis.ticks = element_blank())))

messi_nested_all_goal_assist$plot[[8]] +
  scale_y_continuous(labels = seq(0, 4, by = 2),
                     breaks = seq(0, 4, by = 2),
                     limits = c(0, 4))
```

- have lolipop and color/fill with different value?
- tooltip with total or avg. xG or xA?

## Messi Passes into the Box

* NO data for 2004/2005 so only 7 levels of seasons

```{r}
messi_passer_nested_box <- messi_passer_box %>% 
  group_by(season_name) %>% 
  nest() %>%
  mutate(plot = map2(
    data, season_name,
    ~ ggplot(data = .x, aes(x = pass_duo)) +
      geom_bar(fill = "#a70042") + 
      scale_x_upset(n_intersections = 10,
                    expand = c(0.01, 0.01)) +
      scale_y_continuous(expand = c(0.04, 0.04)) +
      labs(title = glue::glue("Messi's Passes into the Box ({.y})"),
           subtitle = "Messi with ---",
           caption = "Source: StatsBomb",
           x = NULL, y = "Number of Passes") +
      theme_combmatrix(
        text = element_text(family = "Roboto Condensed", 
                            color = "#004c99"),
        plot.title = element_text(family = "Roboto Condensed", size = 20,
                                  color = "#a70042"),
        plot.subtitle = element_text(family = "Roboto Condensed", size = 16,
                                     color = "#004c99"),
        axis.title = element_text(family = "Roboto Condensed", size = 14,
                                  color = "#004c99"), 
        axis.text.x = element_text(family = "Roboto Condensed", size = 12,
                                   color = "#004c99"),
        axis.text.y = element_text(family = "Roboto Condensed", size = 12,
                                   color = "#004c99"),
        panel.background = element_rect(fill = "white"),
        combmatrix.panel.point.size = 4,
        combmatrix.panel.point.color.fill = "#a70042",
        combmatrix.panel.line.color = "#a70042",
        panel.grid = element_line(color = "black"),
        panel.grid.major.x = element_blank(),
        axis.ticks = element_blank())))

messi_passer_nested_box$plot[[7]] +
  scale_y_continuous(labels = seq(0, 12, by = 2),
                     breaks = seq(0, 12, by = 2),
                     limits = c(0, 12))
```

### 2005-2006

```{r}
messi_passer_nested_box$plot[[1]] +
  scale_y_continuous(labels = seq(0, 12, by = 2),
                     breaks = seq(0, 12, by = 2),
                     limits = c(0, 12))
```

### 2006-2007

```{r}
messi_passer_nested_box$plot[[2]] +
  scale_y_continuous(labels = seq(0, 6, by = 1),
                     breaks = seq(0, 6, by = 1),
                     limits = c(0, 6))
```



### 2007-2008

```{r}
messi_passer_nested_box$plot[[3]] +
  scale_y_continuous(labels = seq(0, 10, by = 2),
                     breaks = seq(0, 10, by = 2),
                     limits = c(0, 10))
```


### 2008-2009

```{r}
messi_passer_nested_box$plot[[4]] +
  scale_y_continuous(labels = seq(0, 20, by = 5),
                     breaks = seq(0, 20, by = 5),
                     limits = c(0, 20))
```


### 2009-2010

```{r}
messi_passer_nested_box$plot[[5]] +
  scale_y_continuous(labels = seq(0, 15, by = 5),
                     breaks = seq(0, 15, by = 5),
                     limits = c(0, 15))
```


### 2010-2011

```{r}
messi_passer_nested_box$plot[[6]] +
  scale_y_continuous(labels = seq(0, 30, by = 10),
                     breaks = seq(0, 30, by = 10),
                     limits = c(0, 30))
```



### 2011-2012

```{r}
messi_passer_nested_box$plot[[7]] +
  scale_y_continuous(labels = seq(0, 12, by = 2),
                     breaks = seq(0, 12, by = 2),
                     limits = c(0, 12))
```


## Messi Passes ALL

```{r}
messi_passer_nested_all <- messi_passer_all %>% 
  group_by(season_name) %>% 
  nest() %>%
  mutate(plot = map2(
    data, season_name,
    ~ ggplot(data = .x, aes(x = pass_duo)) +
      geom_bar(fill = "#a70042") + 
      scale_x_upset(n_intersections = 5,
                    expand = c(0.01, 0.01)) +
      scale_y_continuous(expand = c(0.04, 0.04)) +
      labs(title = glue::glue("Messi's Passes ({.y})"),
           subtitle = "Messi with ---",
           caption = "Source: StatsBomb",
           x = NULL, y = "Number of Passes") +
      theme_combmatrix(
        text = element_text(family = "Roboto Condensed", 
                            color = "#004c99"),
        plot.title = element_text(family = "Roboto Condensed", size = 20,
                                  color = "#a70042"),
        plot.subtitle = element_text(family = "Roboto Condensed", size = 16,
                                     color = "#004c99"),
        axis.title = element_text(family = "Roboto Condensed", size = 14,
                                  color = "#004c99"), 
        axis.text.x = element_text(family = "Roboto Condensed", size = 12,
                                   color = "#004c99"),
        axis.text.y = element_text(family = "Roboto Condensed", size = 12,
                                   color = "#004c99"),
        panel.background = element_rect(fill = "white"),
        combmatrix.panel.point.size = 4,
        combmatrix.panel.point.color.fill = "#a70042",
        combmatrix.panel.line.color = "#a70042",
        panel.grid = element_line(color = "black"),
        panel.grid.major.x = element_blank(),
        axis.ticks = element_blank())))

messi_passer_nested_all$plot[[7]] +
  scale_y_continuous(labels = seq(0, 225, by = 50),
                     breaks = seq(0, 225, by = 50),
                     limits = c(0, 225))
```

### 2004-2005

```{r}
messi_passer_nested_all$plot[[1]] +
  scale_y_continuous(labels = seq(0, 4, by = 2),
                     breaks = seq(0, 4, by = 2),
                     limits = c(0, 4))
```

### 2005-2006

```{r}
messi_passer_nested_all$plot[[2]] +
  scale_y_continuous(labels = seq(0, 30, by = 5),
                     breaks = seq(0, 30, by = 5),
                     limits = c(0, 30))
```


### 2006-2007

```{r}
messi_passer_nested_all$plot[[3]] +
  scale_y_continuous(labels = seq(0, 100, by = 20),
                     breaks = seq(0, 100, by = 20),
                     limits = c(0, 100))
```


### 2007-2008

```{r}
messi_passer_nested_all$plot[[4]] +
  scale_y_continuous(labels = seq(0, 100, by = 20),
                     breaks = seq(0, 100, by = 20),
                     limits = c(0, 100))
```


### 2008-2009

```{r}
messi_passer_nested_all$plot[[5]] +
  scale_y_continuous(labels = seq(0, 150, by = 50),
                     breaks = seq(0, 150, by = 50),
                     limits = c(0, 150))
```


### 2009-2010

```{r}
messi_passer_nested_all$plot[[6]] +
  scale_y_continuous(labels = seq(0, 200, by = 50),
                     breaks = seq(0, 200, by = 50),
                     limits = c(0, 200))
```


### 2010-2011


```{r}
messi_passer_nested_all$plot[[7]] +
  scale_y_continuous(labels = seq(0, 225, by = 50),
                     breaks = seq(0, 225, by = 50),
                     limits = c(0, 225))
```


### 2011-2012

```{r}
messi_passer_nested_all$plot[[8]] +
  scale_y_continuous(labels = seq(0, 200, by = 50),
                     breaks = seq(0, 200, by = 50),
                     limits = c(0, 200))
```



















