---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages
```{r, message=FALSE, warning=FALSE}
pacman::p_load(tidyverse, polite, scales, ggimage, rvest, 
               glue, extrafont, showtext, ggrepel, magick, 
               ggforce, lubridate, cowplot, patchwork, rlang)
loadfonts()
```

# functions

## add_logo functions

```{r}
add_logo <- function(plot_path, logo_path, logo_position, logo_scale = 10){

    # Requires magick R Package https://github.com/ropensci/magick

    # Useful error message for logo position
    if (!logo_position %in% c("top right", "top left", "bottom right", "bottom left")) {
        stop("Error Message: Uh oh! Logo Position not recognized\n  Try: logo_positon = 'top left', 'top right', 'bottom left', or 'bottom right'")
    }

    # read in raw images
    plot <- magick::image_read(plot_path)
    logo_raw <- magick::image_read(logo_path)

    # get dimensions of plot for scaling
    plot_height <- magick::image_info(plot)$height
    plot_width <- magick::image_info(plot)$width

    # default scale to 1/10th width of plot
    # Can change with logo_scale
    logo <- magick::image_scale(logo_raw, as.character(plot_width/logo_scale))

    # Get width of logo
    logo_width <- magick::image_info(logo)$width
    logo_height <- magick::image_info(logo)$height

    # Set position of logo
    # Position starts at 0,0 at top left
    # Using 0.01 for 1% - aesthetic padding

    if (logo_position == "top right") {
        x_pos = plot_width - logo_width - 0.01 * plot_width
        y_pos = 0.01 * plot_height
    } else if (logo_position == "top left") {
        x_pos = 0.01 * plot_width
        y_pos = 0.01 * plot_height
    } else if (logo_position == "bottom right") {
        x_pos = plot_width - logo_width - 0.01 * plot_width
        y_pos = plot_height - logo_height - 0.01 * plot_height
    } else if (logo_position == "bottom left") {
        x_pos = 0.01 * plot_width
        y_pos = plot_height - logo_height - 0.01 * plot_height
    }

    # Compose the actual overlay
    magick::image_composite(plot, logo, offset = paste0("+", x_pos, "+", y_pos))

}
```

## tategaki function

```{r}
tategaki <- function(x){
  x <- chartr("ー", "丨", x) # 長音符の処理
  x <- strsplit(split="", x)
  sapply(x, paste, collapse="\n")
}

tategaki_alt <- function(x){
  x <- stringr::str_replace_all(x, "ー", "丨") # 長音符の処理
  stringr::str_wrap(x, width = 1)
}
```




# FC Tokyo

## scrape Tokyo

```{r}
session <- bow("https://www.transfermarkt.com/fc-tokyo/leistungsdaten/verein/6631/plus/0?reldata=JAP1%262018")

print(session)

# grab name from photo element instead
result_name <- scrape(session) %>% 
  html_nodes("#yw1 .bilderrahmen-fixed") %>% 
  html_attr("title") 

# grab age
result_age <- scrape(session) %>% 
  html_nodes(".posrela+ .zentriert") %>% 
  html_text()

# grab minutes played in league
result_mins <- scrape(session) %>% 
  html_nodes("td.rechts") %>% 
  html_text()
```


## scrape length

```{r}
session <- bow("https://www.transfermarkt.com/fc-tokyo/kader/verein/6631/plus/1/galerie/0?saison_id=2018")

result_name2 <- scrape(session) %>% 
  html_nodes("#yw1 .bilderrahmen-fixed") %>% 
  html_attr("title") 

result_bday <- scrape(session) %>% 
  html_nodes(".posrela+ .zentriert") %>% 
  html_text()

result_joinedteam <- scrape(session) %>% 
  html_nodes("td:nth-child(8)") %>% 
  html_text()

result_leaveteam <- scrape(session) %>% 
  html_nodes("td:nth-child(10)") %>% 
  html_text()
```





## clean tokyo

```{r}
# place each vector into list
resultados <- list(result_name, result_age, result_mins)

col_name <- c("name", "age", "minutes")

results_comb <- resultados %>% 
  reduce(cbind) %>% 
  as_tibble() %>% 
  set_names(col_name)

## join + bday
resultados2 <- list(result_name2, result_bday, 
                    result_joinedteam, result_leaveteam)

col_name2 <- c("name", "bday", "join", "leave")

results_comb2 <- resultados2 %>% 
  reduce(cbind) %>% 
  as_tibble() %>% 
  set_names(col_name2)

## combine BOTH
results_comb <- results_comb %>% 
  left_join(results_comb2) 

# fix "strings" into proper formats, calculate % of minutes appeared
tokyo_minutes <- results_comb %>% 
  mutate(age = as.numeric(age),
         minutes = minutes %>% 
           str_replace("\\.", "") %>% 
           str_replace("'", "") %>% 
           as.numeric(),
         min_perc = (minutes / 3060) %>% round(digits = 3),
         bday = str_replace_all(bday, "\\(.*\\)", "") %>% mdy(),
         join = join %>% mdy(),
         join_age = case_when(
           name == "Hirotaka Mita" ~ 29,
           TRUE ~ interval(bday, join) / years(1)),
         age_now = case_when(
           name == "Takefusa Kubo" ~ 17,
           TRUE ~ interval(bday, Sys.Date()) / years(1))) %>% 
  filter(!is.na(minutes)) %>% 
  separate(name, into = c("first_name", "last_name"), 
           sep = " ", fill = "left") %>%
  mutate(join_age = case_when(
           last_name == "Oh" ~ 29,
           TRUE ~ join_age),
         fname = if_else(!is.na(first_name), 
                         str_extract(first_name, "[A-Z]{1}"),
                         ""),
         player = case_when(
    !is.na(first_name) ~ glue("{fname}. {last_name}"),
    TRUE ~ last_name),
    team_name = "FC Tokyo") %>% 
  arrange(desc(min_perc))

glimpse(tokyo_minutes)
```

```{r}
saveRDS(tokyo_minutes, here::here("data/FCTokyo_2019_age_utility_df.RDS"))
```



## plot Tokyo

"ピーク年齢"

```{r fig.height=8, fig.width=12}
# font_add_google("Noto Sans", "Noto Sans")
# showtext_auto()

# rectanglular highlight for players in their prime:
rect_df <- data.frame(
  xmin = 25, xmax = 29,
  ymin = 0, ymax = 1
)

fctokyo_plot <- tokyo_minutes %>% 
  ggplot(aes(x = age_now, y = min_perc)) +
  geom_vline(xintercept = 25, alpha = 0.4, color = "grey20") +
  geom_hline(yintercept = 0.5, alpha = 0.4, color = "grey20") +
  geom_rect(data = rect_df,
            aes(x = NULL, y = NULL,
                xmin = xmin, xmax = xmax,
                ymin = ymin, ymax = ymax),
            fill = "#271672", alpha = 0.4) +
  geom_link(aes(x = join_age, xend = age_now,
                y = min_perc, yend = min_perc,
                alpha = stat(index)), 
            color = "#DD2220", size = 1.75) + 
  geom_point(aes(x = age_now), color = "#DD2220", size = 3.5) +
  geom_text_repel(
    aes(label = player),
    nudge_y = 0.01, 
    seed = 6) + 
  annotate("text", x = 27, y = 1.055,
           size = 5.5, fontface = "bold",
           family = "Yu Mincho Demibold",
           label = "ピーク年齢", color = "grey20") +
  scale_y_continuous(
    expand = c(0.01, 0),
    limits = c(0, 1.08), 
    breaks = seq(0, 1, by = 0.2), 
    labels = percent_format()) +
  scale_x_continuous(
    limits = c(16, 33),
    breaks = seq(18, 34, by = 2)) +
  labs(
    x = "年齢", 
    y = tategaki_alt("出場時間 (%)"),  
    title = "FC東京: 年齢-出場時間",
    subtitle = "J-League 2019 Season (100% = 3060分)") +
  theme_bw() +
  theme(
    text = element_text(family = "Yu Mincho Demibold"),
    panel.border = element_blank(),
    plot.title = element_text(color = "#271672", size = 20, face = "bold"),
    plot.subtitle = element_text(color = "#DD2220", size = 18),
    plot.caption = element_text(size = 14),
    panel.grid.minor = element_blank(),
    axis.title.y = element_text(angle = 0, vjust= 0.5),
    axis.title = element_text(size = 16),
    axis.text = element_text(size = 14),
    axis.ticks = element_blank(),
    legend.position = "none")

fctokyo_plot
```

```{r}
ggsave(plot = fctokyo_plot, "../J-League 2020/output/fctokyo_plot.png",
       height = 8, width = 12)
```



```{r}
plot_logo <- add_logo(plot_path = "../J-League 2020/output/fctokyo_plot.png",
                      logo_path = "https://upload.wikimedia.org/wikipedia/en/4/45/FCTokyo.png",
                      logo_position = "top right",
                      logo_scale = 23)

plot_logo
```

```{r}
image_write(image = plot_logo, "../J-League 2020/output/fctokyo_logo_plot.png")
```


## legend plot

```{r fig.width=3, fig.height=5}
leg_df <- tibble(x = 23, xend = 28,
                 y = 0.65, yend = 0.65)


legend_plot <- tokyo_minutes %>% 
  ggplot(aes(x = age_now, y = min_perc)) +
  geom_rect(data = rect_df,
            aes(x = NULL, y = NULL,
                xmin = xmin, xmax = xmax,
                ymin = ymin, ymax = ymax),
            fill = "#271672", alpha = 0.4) +
  geom_link(data = leg_df,
            aes(x = x, xend = xend,
                y = y, yend = yend,
                alpha = stat(index)), 
            color = "#DD2220", size = 1.75) + 
  geom_point(x = 28, y = 0.65, color = "#DD2220", size = 3.5) +
  ## top arrow
  geom_curve(x = 30, xend = 28.4,
             y = 0.77, yend = 0.65,
             curvature = -0.5, size = 1.2,
             arrow = arrow(length = unit(0.1, "inches")),
             lineend = "round") +
  ## bottom arrow
  geom_segment(x = 23, xend = 23,
               y = 0.48, yend = 0.63,
               size = 1.2,
               arrow = arrow(length = unit(0.1, "inches")),
               lineend = "round") +
  annotate("text", x = 30, y = 0.83, family = "Yu Mincho Demibold",
           label = "年齢", size = 4.5) +
  annotate("text", x = 23, y = 0.4, family = "Yu Mincho Demibold",
           label = "年齢 （入団時）", size = 4.5) +
  scale_y_continuous(
    limits = c(0, 1.05), 
    breaks = seq(0, 1, by = 0.2),
    labels = percent_format()) +
  scale_x_continuous(
    limits = c(18, 33),
    breaks = seq(18, 34, by = 2)) +
  labs(caption = glue("
                   データ: transfermarkt.com
                   作: @R_by_Ryo")) +
  theme_bw() +
  theme(
    text = element_text(family = "Yu Mincho Demibold"),
    panel.border = element_blank(),
    plot.caption = element_text(size = 14),
    axis.ticks = element_blank(),
    axis.title = element_blank(),
    axis.text = element_text(size = 10),
    legend.position = "none")

legend_plot
```



## age histogram


```{r fig.width=3, fig.height=5}
tokyo_minutes %>% 
  mutate(team = "FC Tokyo") %>% 
  select(team, age) %>% 
  #spread("team", "age") %>% 
  ggplot(aes(x = age, y = team), groupOnX = TRUE) +
  ggbeeswarm::geom_beeswarm()


tokyo_minutes %>% 
  ggplot(aes(age)) +
  geom_freqpoly(binwidth = 1.5)


tokyo_minutes %>% 
  mutate(team = "FC Tokyo") %>% 
  ggplot(aes(age, team)) +
  ggridges::geom_density_ridges(scale = 4) +
  scale_y_discrete(expand = c(0.05, 0))


tokyo_minutes %>% 
  add_count(age) %>% 
  ggplot(aes(as.factor(age), n)) +
  ggridges::geom_density_ridges()
  mutate(team = "FC Tokyo") %>% 
  group_by(age) %>% 
  summarize(tot = n()) %>% 
  ungroup() %>% 
  ggplot(aes(age, tot, height = tot)) +
  ggridges::geom_ridgeline()
  
  
tokyo_minutes %>% 
  add_count(age) %>% 
  ggplot(aes(as.factor(age), n)) +
  geom_col()

tokyo_minutes %>% 
  ggplot(aes(age)) +
  geom_density(#aes(y = ..count..), 
               fill = "grey20") +
  geom_vline(aes(xintercept = median(age)), color = "red") +
  scale_x_continuous(limits = c(8, 40)) +
  scale_y_continuous(limits = c(0, 0.1))
```


## summary stats

```{r fig.width=3, fig.height=5}
tokyo_minutes %>% 
  mutate(duration = age_now - join_age) %>% 
  summarize(median_age = median(age),
            median_duration = median(duration),
            sum_players = n())
```

```{r fig.width=3, fig.height=5}
summary_stats <- tokyo_minutes %>%
  ggplot(aes(x = age_now, y = min_perc)) +
  annotate("text", x = 25, y = 0.75, 
           size = 4,
           label = "Number of Players: 25",
           family = "Yu Mincho Demibold") +
  annotate("text", x = 25, y = 0.65, 
           size = 4,
           label = "Median Age: 24",
           family = "Yu Mincho Demibold") +
  annotate("text", x = 25, y = 0.55, 
           size = 4,
           label = "Median Length of Stay: 2.59 Years",
           family = "Yu Mincho Demibold") +
  theme_void()

summary_stats
```


## combine


```{r fig.height=8, fig.width=12}
fctokyo_plot +
  theme(plot.margin = unit(c(1, 10, 1, 1), "cm"))

legend_plot
```




```{r fig.width=15, fig.height=8}
ggdraw(plot_grid(fctokyo_plot, legend_plot, 
                 rel_heights = c(2, 1)))


ggdraw() +
  draw_plot(fctokyo_plot) +
  draw_plot(legend_plot, hjust = 10, 
            width = 0.13, height = 0.2)


ggdraw(fctokyo_plot +
  theme(plot.margin = unit(c(1, 10, 1, 1), "cm"))) +
  draw_plot(legend_plot, 1, 0,
            width = 0.13, height = 0.2)
```



```{r fig.width=15, fig.height=8}
layout <- "
AAAA##
AAAAC#
AAAA##
AAAAB#
"

combined_plot <- fctokyo_plot + legend_plot + summary_stats + 
  plot_layout(design = layout)

combined_plot
```

## save

```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/fctokyo_combplot.png",
       height = 8, width = 15)
```



```{r}
plot_logo <- add_logo(plot_path = "../J-League 2020/output/fctokyo_combplot.png",
                      logo_path = "https://upload.wikimedia.org/wikipedia/en/4/45/FCTokyo.png",
                      logo_position = "top right",
                      logo_scale = 23)

plot_logo
```

```{r}
image_write(image = plot_logo, "../J-League 2020/output/fctokyo_logo_combplot.png")
```



# Kashiwa Reysol

## scrape reysol

```{r}
session <- bow("https://www.transfermarkt.com/kashiwa-reysol/leistungsdaten/verein/6632/plus/1?reldata=JAP2%262018")

print(session)

# grab name from photo element instead
result_name <- scrape(session) %>% 
  html_nodes("#yw1 .bilderrahmen-fixed") %>% 
  html_attr("title") 

# grab age
result_age <- scrape(session) %>% 
  html_nodes(".posrela+ .zentriert") %>% 
  html_text()

# grab minutes played in league
result_mins <- scrape(session) %>% 
  html_nodes("td.rechts") %>% 
  html_text()
```


## scrape length

```{r}
session <- bow("https://www.transfermarkt.com/kashiwa-reysol/kader/verein/6632/plus/1/galerie/0?saison_id=2018")

result_name2 <- scrape(session) %>% 
  html_nodes("#yw1 .bilderrahmen-fixed") %>% 
  html_attr("title") 

result_bday <- scrape(session) %>% 
  html_nodes(".posrela+ .zentriert") %>% 
  html_text()

result_joinedteam <- scrape(session) %>% 
  html_nodes("td:nth-child(8)") %>% 
  html_text()

result_leaveteam <- scrape(session) %>% 
  html_nodes("td:nth-child(10)") %>% 
  html_text()
```





## clean reysol

```{r}
# place each vector into list
resultados <- list(result_name, result_age, result_mins)

col_name <- c("name", "age", "minutes")

results_comb <- resultados %>% 
  reduce(cbind) %>% 
  as_tibble() %>% 
  set_names(col_name)

## join + bday
resultados2 <- list(result_name2, result_bday, 
                    result_joinedteam, result_leaveteam)

col_name2 <- c("name", "bday", "join", "leave")

results_comb2 <- resultados2 %>% 
  reduce(cbind) %>% 
  as_tibble() %>% 
  set_names(col_name2)

## combine BOTH
results_comb <- results_comb %>% 
  left_join(results_comb2) 

# fix "strings" into proper formats, calculate % of minutes appeared
reysol_minutes <- results_comb %>% 
  mutate(age = as.numeric(age),
         minutes = minutes %>% 
           str_replace("\\.", "") %>% 
           str_replace("'", "") %>% 
           as.numeric(),
         min_perc = (minutes / 3060) %>% round(digits = 3),
         bday = str_replace_all(bday, "\\(.*\\)", "") %>% mdy(),
         join = join %>% mdy(),
         join_age = case_when(
           name == "Hirotaka Mita" ~ 29,
           TRUE ~ interval(bday, join) / years(1)),
         age_now = case_when(
           name == "Takefusa Kubo" ~ 17,
           TRUE ~ interval(bday, Sys.Date()) / years(1))) %>% 
  filter(!is.na(minutes)) %>% 
  separate(name, into = c("first_name", "last_name"), 
           sep = " ", fill = "left") %>%
  mutate(join_age = case_when(
           last_name == "Oh" ~ 29,
           TRUE ~ join_age),
         fname = if_else(!is.na(first_name), 
                         str_extract(first_name, "[A-Z]{1}"),
                         ""),
         player = case_when(
    !is.na(first_name) ~ glue("{fname}. {last_name}"),
    TRUE ~ last_name),
    team_name = "Kashiwa Reysol") %>% 
  arrange(desc(min_perc))

glimpse(reysol_minutes)
```




# Jubilo Iwata

## scrape jubilo

```{r}
session <- bow("https://www.transfermarkt.com/jubilo-iwata/leistungsdaten/verein/937/plus/1?reldata=JAP1%262018")

print(session)

# grab name from photo element instead
result_name <- scrape(session) %>% 
  html_nodes("#yw1 .bilderrahmen-fixed") %>% 
  html_attr("title") 

# grab age
result_age <- scrape(session) %>% 
  html_nodes(".posrela+ .zentriert") %>% 
  html_text()

# grab minutes played in league
result_mins <- scrape(session) %>% 
  html_nodes("td.rechts") %>% 
  html_text()
```


## scrape length

```{r}
session <- bow("https://www.transfermarkt.com/jubilo-iwata/kader/verein/937/saison_id/2018/plus/1")

result_name2 <- scrape(session) %>% 
  html_nodes("#yw1 .bilderrahmen-fixed") %>% 
  html_attr("title") 

result_bday <- scrape(session) %>% 
  html_nodes(".posrela+ .zentriert") %>% 
  html_text()

result_joinedteam <- scrape(session) %>% 
  html_nodes("td:nth-child(8)") %>% 
  html_text()

result_leaveteam <- scrape(session) %>% 
  html_nodes("td:nth-child(10)") %>% 
  html_text()
```

## clean jubilo

```{r}
# place each vector into list
resultados <- list(result_name, result_age, result_mins)

col_name <- c("name", "age", "minutes")

results_comb <- resultados %>% 
  reduce(cbind) %>% 
  as_tibble() %>% 
  set_names(col_name)

## join + bday
resultados2 <- list(result_name2, result_bday, 
                    result_joinedteam, result_leaveteam)

col_name2 <- c("name", "bday", "join", "leave")

results_comb2 <- resultados2 %>% 
  reduce(cbind) %>% 
  as_tibble() %>% 
  set_names(col_name2)

## combine BOTH
results_comb <- results_comb %>% 
  left_join(results_comb2) 

# fix "strings" into proper formats, calculate % of minutes appeared
jubilo_minutes <- results_comb %>% 
  mutate(age = as.numeric(age),
         minutes = minutes %>% 
           str_replace("\\.", "") %>% 
           str_replace("'", "") %>% 
           as.numeric(),
         min_perc = (minutes / 3060) %>% round(digits = 3),
         bday = str_replace_all(bday, "\\(.*\\)", "") %>% mdy(),
         join = join %>% mdy(),
         join_age = case_when(
           name == "Hirotaka Mita" ~ 29,
           TRUE ~ interval(bday, join) / years(1)),
         age_now = case_when(
           name == "Takefusa Kubo" ~ 17,
           TRUE ~ interval(bday, Sys.Date()) / years(1))) %>% 
  filter(!is.na(minutes)) %>% 
  separate(name, into = c("first_name", "last_name"), 
           sep = " ", fill = "left") %>%
  mutate(join_age = case_when(
           last_name == "Oh" ~ 29,
           TRUE ~ join_age),
         fname = if_else(!is.na(first_name), 
                         str_extract(first_name, "[A-Z]{1}"),
                         ""),
         player = case_when(
    !is.na(first_name) ~ glue("{fname}. {last_name}"),
    TRUE ~ last_name),
    team_name = "Jubilo Iwata") %>% 
  arrange(desc(min_perc))

glimpse(jubilo_minutes)
```




# Matsumoto Yamagaa

## scrape yamaga

```{r}
session <- bow("https://www.transfermarkt.com/matsumoto-yamaga/leistungsdaten/verein/25765/plus/1?reldata=JAP1%262018")

print(session)

# grab name from photo element instead
result_name <- scrape(session) %>% 
  html_nodes("#yw1 .bilderrahmen-fixed") %>% 
  html_attr("title") 

# grab age
result_age <- scrape(session) %>% 
  html_nodes(".posrela+ .zentriert") %>% 
  html_text()

# grab minutes played in league
result_mins <- scrape(session) %>% 
  html_nodes("td.rechts") %>% 
  html_text()
```


## scrape length

```{r}
session <- bow("https://www.transfermarkt.com/matsumoto-yamaga/kader/verein/25765/saison_id/2018/plus/1")

result_name2 <- scrape(session) %>% 
  html_nodes("#yw1 .bilderrahmen-fixed") %>% 
  html_attr("title") 

result_bday <- scrape(session) %>% 
  html_nodes(".posrela+ .zentriert") %>% 
  html_text()

result_joinedteam <- scrape(session) %>% 
  html_nodes("td:nth-child(8)") %>% 
  html_text()

result_leaveteam <- scrape(session) %>% 
  html_nodes("td:nth-child(10)") %>% 
  html_text()
```

## clean yamaga

```{r}
# place each vector into list
resultados <- list(result_name, result_age, result_mins)

col_name <- c("name", "age", "minutes")

results_comb <- resultados %>% 
  reduce(cbind) %>% 
  as_tibble() %>% 
  set_names(col_name)

## join + bday
resultados2 <- list(result_name2, result_bday, 
                    result_joinedteam, result_leaveteam)

col_name2 <- c("name", "bday", "join", "leave")

results_comb2 <- resultados2 %>% 
  reduce(cbind) %>% 
  as_tibble() %>% 
  set_names(col_name2)

## combine BOTH
results_comb <- results_comb %>% 
  left_join(results_comb2) 

# fix "strings" into proper formats, calculate % of minutes appeared
yamaga_minutes <- results_comb %>% 
  mutate(age = as.numeric(age),
         minutes = minutes %>% 
           str_replace("\\.", "") %>% 
           str_replace("'", "") %>% 
           as.numeric(),
         min_perc = (minutes / 3060) %>% round(digits = 3),
         bday = str_replace_all(bday, "\\(.*\\)", "") %>% mdy(),
         join = join %>% mdy(),
         join_age = case_when(
           name == "Hirotaka Mita" ~ 29,
           TRUE ~ interval(bday, join) / years(1)),
         age_now = case_when(
           name == "Takefusa Kubo" ~ 17,
           TRUE ~ interval(bday, Sys.Date()) / years(1))) %>% 
  filter(!is.na(minutes)) %>% 
  separate(name, into = c("first_name", "last_name"), 
           sep = " ", fill = "left") %>%
  mutate(join_age = case_when(
           last_name == "Oh" ~ 29,
           TRUE ~ join_age),
         fname = if_else(!is.na(first_name), 
                         str_extract(first_name, "[A-Z]{1}"),
                         ""),
         player = case_when(
    !is.na(first_name) ~ glue("{fname}. {last_name}"),
    TRUE ~ last_name),
    team_name = "Matsumoto Yamaga") %>% 
  arrange(desc(min_perc))

glimpse(yamaga_minutes)
```















# all teams

## web-scrape

### team links function

```{r}
get_team_links <- function(season) {
  
  url <- "https://www.transfermarkt.com/j1-league/startseite/wettbewerb/JAP1/plus/?saison_id={season}"
  
  session <- bow(url)
  
  team_links <- scrape(session) %>% 
    html_nodes("#yw1 > table > tbody > tr > td.zentriert.no-border-rechts > a") %>% 
    html_attr("href")
  
 # season <- enquo(season)
  
  team_links_df <- team_links %>% 
    enframe(name = NULL) %>% 
    separate(value, c(NA, "team_name", NA, NA, "team_num", NA, NA), sep = "/") %>% 
    mutate(link = glue("https://www.transfermarkt.com/{team_name}/leistungsdaten/verein/{team_num}/reldata/JAP1%26{season}/plus/1"),
           season = season)
}
```

```{r}
team_links_df <- get_team_links(season = 2018)

glimpse(team_links_df)
```

### scrape function

```{r}
jleague_age_utility_info <- function(team_name, team_num, season) {
  ## get age + minutes played
  session <- bow(glue::glue("https://www.transfermarkt.com/{team_name}/leistungsdaten/verein/{team_num}/plus/0?reldata=JAP1%26{season}"))
  
  # grab name from photo element instead
  result_name <- scrape(session) %>% 
    html_nodes("#yw1 .bilderrahmen-fixed") %>% 
    html_attr("title") 
  
  # grab age
  result_age <- scrape(session) %>% 
    html_nodes(".posrela+ .zentriert") %>% 
    html_text()
  
  # grab minutes played in league
  result_mins <- scrape(session) %>% 
    html_nodes("td.rechts") %>% 
    html_text()
  
  ## get length
  session <- bow(glue::glue("https://www.transfermarkt.com/{team_name}/kader/verein/{team_num}/plus/1/galerie/0?saison_id={season}"))
  
  result_name2 <- scrape(session) %>% 
    html_nodes("#yw1 .bilderrahmen-fixed") %>% 
    html_attr("title") 
  
  result_bday <- scrape(session) %>% 
    html_nodes(".posrela+ .zentriert") %>% 
    html_text()
  
  result_joinedteam <- scrape(session) %>% 
    html_nodes("td:nth-child(8)") %>% 
    html_text()
  
  result_leaveteam <- scrape(session) %>% 
    html_nodes("td:nth-child(10)") %>% 
    html_text()
  
  # place each vector into list
  resultados <- list(result_name, result_age, result_mins)
  
  col_name <- c("name", "age", "minutes")
  
  results_comb <- resultados %>% 
    reduce(cbind) %>% 
    as_tibble() %>% 
    set_names(col_name)
  
  ## join + bday
  resultados2 <- list(result_name2, result_bday, 
                      result_joinedteam, result_leaveteam)
  
  col_name2 <- c("name", "bday", "join", "leave")
  
  results_comb2 <- resultados2 %>% 
    reduce(cbind) %>% 
    as_tibble() %>% 
    set_names(col_name2)
  
  ## combine BOTH
  results_comb <- results_comb %>% 
    left_join(results_comb2) 
  
  # fix "strings" into proper formats, calculate % of minutes appeared
  all_team_minutes <- results_comb %>% 
    mutate(age = as.numeric(age),
           minutes = minutes %>% 
             str_replace("\\.", "") %>% 
             str_replace("'", "") %>% 
             as.numeric(),
           min_perc = (minutes / 3060) %>% round(digits = 3),
           bday = str_replace_all(bday, "\\(.*\\)", "") %>% mdy(),
           join = join %>% mdy(),
           join_age = interval(bday, join) / years(1),
           age_now = interval(bday, Sys.Date()) / years(1)) %>% 
    filter(!is.na(minutes)) %>% 
    separate(name, into = c("first_name", "last_name"), 
             sep = " ", fill = "left") %>%
    mutate(
      fname = if_else(!is.na(first_name), 
                      str_extract(first_name, "[A-Z]{1}"),
                      ""),
      player = case_when(
        !is.na(first_name) ~ glue("{fname}. {last_name}"),
        TRUE ~ last_name),
      team_name = team_name,
      team_name = case_when(
        team_name == "shimizu-s-pulse" ~ "Shimizu S-Pulse",
        team_name == "fc-tokyo" ~ "FC Tokyo", 
        team_name == "yokohama-f-marinos" ~ "Yokohama F. Marinos",
        TRUE ~ str_replace_all(team_name, "-", " ") %>% stringr::str_to_title()),
      season = season) %>% 
    arrange(desc(min_perc)) 
  
  return(all_team_minutes)
}
```

```{r}
# ALL 18 TEAMS AT ONCE, WILL TAKE A WHILE:
age_utility_df_ALL <- pmap(list(team_links_df$team_name, 
                                team_links_df$team_num,
                                team_links_df$season),
                             .f = jleague_age_utility_info)

jleague_age_utility_df <- age_utility_df_ALL %>% 
  reduce(rbind)

## save
saveRDS(jleague_age_utility_df, file = glue("{here::here()}/data/jleague_age_utility_df_2019.RDS"))
```

# all team data

```{r}
jleague_age_utility_df <- readRDS(file = here::here("data/jleague_age_utility_df_2019.RDS"))
```



## Vissel Kobe: main plot

```{r}
jleague_age_utility_df %>% 
  filter(team_name == "Vissel Kobe")
```

```{r}
create_age_utility_plot <- function(df, color_1, color_2) {
  
  rect_df <- data.frame(
    xmin = 25, xmax = 29,
    ymin = 0, ymax = 1
  )
  max <- max(df$age, na.rm = TRUE)
  lims <- c(16, (max(df$age, na.rm = TRUE) + 2))
  breaks <- seq(from = 18, to = max, by = 2)
  
  plot <- df %>% 
    ggplot(aes(x = age_now, y = min_perc)) +
    geom_vline(xintercept = 25, alpha = 0.4, color = "grey20") +
    geom_hline(yintercept = 0.5, alpha = 0.4, color = "grey20") +
    geom_rect(data = rect_df,
              aes(x = NULL, y = NULL,
                  xmin = xmin, xmax = xmax,
                  ymin = ymin, ymax = ymax),
              fill = color_1, alpha = 0.4) +
    geom_link(aes(x = join_age, xend = age_now,
                  y = min_perc, yend = min_perc,
                  alpha = stat(index)), 
              color = color_2, size = 1.75) + 
    geom_point(aes(x = age_now), color = color_2, size = 3.5) +
    geom_text_repel(
      aes(label = player),
      nudge_y = 0.01, 
      seed = 6) + 
    annotate("text", x = 27, y = 1.055,
             size = 5.5, fontface = "bold",
             family = "Yu Mincho Demibold",
             label = "ピーク年齢", color = "grey20") +
    scale_y_continuous(
      expand = c(0.01, 0),
      limits = c(0, 1.08), 
      breaks = seq(0, 1, by = 0.2), 
      labels = percent_format()) +
    scale_x_continuous(
      limits = lims,
      breaks = breaks) +
    labs(
      x = "年齢", 
      y = tategaki_alt("出場時間 (%)"),  
      title = glue("{df$team_name}: 年齢-出場時間"),
      subtitle = "J-League 2019 Season (100% = 3060分)") +
    theme_bw() +
    theme(
      text = element_text(family = "Yu Mincho Demibold"),
      panel.border = element_blank(),
      plot.title = element_text(color = color_1, size = 20, face = "bold"),
      plot.subtitle = element_text(color = color_2, size = 18),
      plot.caption = element_text(size = 14),
      panel.grid.minor = element_blank(),
      axis.title.y = element_text(angle = 0, vjust= 0.5),
      axis.title = element_text(size = 16),
      axis.text = element_text(size = 14),
      axis.ticks = element_blank(),
      legend.position = "none")
  
  return(plot)
}


```



```{r fig.height=8, fig.width=12}
df <- jleague_age_utility_df %>% 
  filter(team_name == "Vissel Kobe")

vk_plot <- df %>% 
  create_age_utility_plot(color_1 = "#8B0000", color_2 = "#000000")

vk_plot
```


## legend plot

```{r fig.width=3, fig.height=5}
create_age_utility_legend <- function(df, color_1, color_2){
  
  rect_df <- data.frame(
    xmin = 25, xmax = 29,
    ymin = 0, ymax = 1
  )
  
  leg_df <- tibble(
    x = 23, xend = 28,
    y = 0.65, yend = 0.65
  )
  
  legend_plot <- df %>% 
    ggplot(aes(x = age_now, y = min_perc)) +
    geom_rect(data = rect_df,
              aes(x = NULL, y = NULL,
                  xmin = xmin, xmax = xmax,
                  ymin = ymin, ymax = ymax),
              fill = color_1, alpha = 0.4) +
    geom_link(data = leg_df,
              aes(x = x, xend = xend,
                  y = y, yend = yend,
                  alpha = stat(index)), 
              color = color_2, size = 1.75) + 
    geom_point(x = 28, y = 0.65, color = color_2, size = 3.5) +
    ## top arrow
    geom_curve(x = 30, xend = 28.4,
               y = 0.77, yend = 0.65,
               curvature = -0.5, size = 1.2,
               arrow = arrow(length = unit(0.1, "inches")),
               lineend = "round") +
    ## bottom arrow
    geom_segment(x = 23, xend = 23,
                 y = 0.48, yend = 0.63,
                 size = 1.2,
                 arrow = arrow(length = unit(0.1, "inches")),
                 lineend = "round") +
    annotate("text", x = 30, y = 0.83, family = "Yu Mincho Demibold",
             label = "年齢", size = 4.5) +
    annotate("text", x = 23, y = 0.4, family = "Yu Mincho Demibold",
             label = "年齢 （入団時）", size = 4.5) +
    scale_y_continuous(
      limits = c(0, 1.05), 
      breaks = seq(0, 1, by = 0.2),
      labels = percent_format()) +
    scale_x_continuous(
      limits = c(18, 33),
      breaks = seq(18, 34, by = 2)) +
    labs(caption = glue("
                   データ: transfermarkt.com
                   作: @R_by_Ryo")) +
    theme_bw() +
    theme(
      text = element_text(family = "Yu Mincho Demibold"),
      panel.border = element_blank(),
      plot.caption = element_text(size = 14),
      axis.ticks = element_blank(),
      axis.title = element_blank(),
      axis.text = element_text(size = 10),
      legend.position = "none")
  
  return(legend_plot)
}
```


```{r fig.width=3, fig.height=5}
vk_leg <- jleague_age_utility_df %>% 
  filter(team_name == "Vissel Kobe") %>% 
  create_age_utility_legend(color_1 = "#8B0000", color_2 = "#000000")

vk_leg
```


## summary stats


```{r fig.width=3, fig.height=5}
create_summary_stats_plot <- function(df) {
  summary_df <- df %>% 
    mutate(duration = age_now - join_age) %>% 
    summarize(median_age = median(age),
              median_duration = round(median(duration, na.rm = TRUE), digits = 2),
              sum_players = n())
  
  summary_stats <- summary_df %>%
    ggplot(aes(x = age_now, y = min_perc)) +
    annotate("text", x = 25, y = 0.75, 
             size = 4,
             label = glue::glue("選手: {summary_df$sum_players}人"),
             family = "Yu Mincho Demibold") +
    annotate("text", x = 25, y = 0.65, 
             size = 4,
             label = glue::glue("平均年齢: {summary_df$median_age}歳"),
             family = "Yu Mincho Demibold") +
    annotate("text", x = 25, y = 0.55, 
             size = 4,
             label = glue::glue("平均滞在期間: {summary_df$median_duration}年"),
             family = "Yu Mincho Demibold") +
    scale_y_continuous(limits = c(0.3, 0.9)) +
    theme_void()
  
  return(summary_stats)
}
```

選手：２５人
平均年齢
平均滞在期間/日数

```{r fig.width=3, fig.height=5}
vk_sum <- jleague_age_utility_df %>% 
  filter(team_name == "Vissel Kobe") %>% 
  create_summary_stats_plot()

vk_sum
```


## combine

```{r fig.width=15, fig.height=8}
layout <- "
AAAA##
AAAAC#
AAAA##
AAAAB#
"

combined_plot <- vk_plot + vk_leg + vk_sum + 
  plot_layout(design = layout)

combined_plot
```

## save

```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/visselkobe_combplot.png",
       height = 8, width = 15)
```



```{r}
plot_logo <- add_logo(plot_path = "../J-League 2020/output/visselkobe_combplot.png",
                      logo_path = "https://upload.wikimedia.org/wikipedia/en/8/87/VisselKobe.png",
                      logo_position = "top right",
                      logo_scale = 23)

plot_logo
```

```{r}
image_write(image = plot_logo, "../J-League 2020/output/visselkobe_logo_combplot.png")
```



# Shimizu S-Pulse

## plot

```{r fig.height=8, fig.width=12}
df <- jleague_age_utility_df %>% 
  filter(team_name == "Shimizu S-Pulse")

ssp_plot <- df %>% 
  create_age_utility_plot(color_1 = "#F29900", color_2 = "#0569AE")

ssp_plot
```

## legend plot

```{r fig.width=3, fig.height=5}
ssp_leg <- jleague_age_utility_df %>% 
  filter(team_name == "Shimizu S-Pulse") %>% 
  create_age_utility_legend(color_1 = "#F29900", color_2 = "#0569AE")

ssp_leg
```

## summary stats

```{r fig.width=3, fig.height=5}
ssp_sum <- jleague_age_utility_df %>% 
  filter(team_name == "Shimizu S-Pulse") %>% 
  create_summary_stats_plot()

ssp_sum
```

## combine

```{r fig.width=15, fig.height=8}
layout <- "
AAAA##
AAAAC#
AAAA##
AAAAB#
"

combined_plot <- ssp_plot + ssp_leg + ssp_sum + 
  plot_layout(design = layout)

combined_plot
```

## save

```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/shimizuspulse_combplot.png",
       height = 8, width = 15)
```



```{r}
plot_logo <- add_logo(plot_path = "../J-League 2020/output/shimizuspulse_combplot.png",
                      logo_path = "https://upload.wikimedia.org/wikipedia/en/e/ef/Shimizu_S-Pulse_emblem_since_2020.png",
                      logo_position = "top right",
                      logo_scale = 23)

plot_logo
```

```{r}
image_write(image = plot_logo, "../J-League 2020/output/shimizuspulse_logo_combplot.png")
```




# Shonan Bellmare

## plot

```{r fig.height=8, fig.width=12}
df <- jleague_age_utility_df %>% 
  filter(team_name == "Shonan Bellmare")

sb_plot <- df %>% 
  create_age_utility_plot(color_1 = "#67B356", color_2 = "#103C95")

sb_plot
```

## legend plot

```{r fig.width=3, fig.height=5}
sb_leg <- jleague_age_utility_df %>% 
  filter(team_name == "Shonan Bellmare") %>% 
  create_age_utility_legend(color_1 = "#67B356", color_2 = "#103C95")

sb_leg
```

## summary stats

```{r fig.width=3, fig.height=5}
sb_sum <- jleague_age_utility_df %>% 
  filter(team_name == "Shonan Bellmare") %>% 
  create_summary_stats_plot()

sb_sum
```

## combine

```{r fig.width=15, fig.height=8}
layout <- "
AAAA##
AAAAC#
AAAA##
AAAAB#
"

combined_plot <- sb_plot + sb_leg + sb_sum + 
  plot_layout(design = layout)

combined_plot
```

## save

```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/shonanbellmare_combplot.png",
       height = 8, width = 15)
```



```{r}
plot_logo <- add_logo(plot_path = "../J-League 2020/output/shonanbellmare_combplot.png",
                      logo_path = "https://upload.wikimedia.org/wikipedia/en/2/2c/ShonanBellmare.png",
                      logo_position = "top right",
                      logo_scale = 23)

plot_logo
```

```{r}
image_write(image = plot_logo, "../J-League 2020/output/shonanbellmare_logo_combplot.png")
```


# Yokohama F. Marinos


## plot

```{r fig.height=8, fig.width=12}
yfm_plot <- jleague_age_utility_df %>% 
  filter(team_name == "Yokohama F. Marinos") %>% 
  create_age_utility_plot(color_1 = "#003f99", color_2 = "#F40041")

yfm_plot
```

## legend plot

```{r fig.width=3, fig.height=5}
yfm_leg <- jleague_age_utility_df %>% 
  filter(team_name == "Yokohama F. Marinos") %>% 
  create_age_utility_legend(color_1 = "#003f99", color_2 = "#F40041")

yfm_leg
```

## summary_plot

```{r fig.width=3, fig.height=5}
yfm_sum <- jleague_age_utility_df %>% 
  filter(team_name == "Yokohama F. Marinos") %>% 
  create_summary_stats_plot()

yfm_sum
```

## combine

```{r fig.width=15, fig.height=8}
layout <- "
AAAA##
AAAAC#
AAAA##
AAAAB#
"

combined_plot <- yfm_plot + yfm_leg + yfm_sum + 
  plot_layout(design = layout)

combined_plot
```

## save


```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/yokohamamarinos_combplot.png",
       height = 8, width = 15)
```



```{r}
plot_logo <- add_logo(plot_path = "../J-League 2020/output/yokohamamarinos_combplot.png",
                      logo_path = "https://upload.wikimedia.org/wikipedia/en/6/65/Yokohama_F_Marinos_logo.svg",
                      logo_position = "top right",
                      logo_scale = 15)

plot_logo
```

```{r}
image_write(image = plot_logo, "../J-League 2020/output/yokohamamarinos_logo_combplot.png")
```


# function


```{r fig.width=15, fig.height=8}
img <- here::here("img/KawasakiFrontale.png")

ggdraw() +
  draw_plot(combined_plot) +
  draw_image(img, x = 0.01, y = 0.01, width = 0.1, height = 0.2)


img <- png::readPNG(here::here("img/KawasakiFrontale.png"))
rasterimg <- grid::rasterGrob(img, interpolate = TRUE)

img_df <- data.frame(x = seq(1, 10, 1),
                     y = seq(1, 10, 1))

logo_plot <- ggplot(img_df, aes(x = x, y = y)) +
  geom_point(color = "white") +
  annotation_custom(rasterimg, xmin = 2, xmax = 8, 
                    ymin = 2, ymax = 8) +
  scale_x_continuous(limits = c(0, 10)) +
  scale_y_continuous(limits = c(0, 10)) +
  theme_void()

logo_plot
```




```{r fig.width=15, fig.height=8}
age_utility_plotter <- function(df, team_name, color_1, color_2) {
  
  team_name <- enquo(team_name)

  df <- df %>% 
  filter(team_name == !!team_name)
  
  age_utility_plot <- df %>% 
    create_age_utility_plot(color_1 = color_1, color_2 = color_2)
  
  plot_leg <- df %>% 
    create_age_utility_legend(color_1 = color_1, color_2 = color_2)
  
  plot_sum <- df %>% 
  create_summary_stats_plot()
  
  layout <- "
AAAA##
AAAAC#
AAAA##
AAAAB#
"
  
  combined_plot <- age_utility_plot + plot_leg + plot_sum + 
    plot_layout(design = layout)
  
  return(combined_plot)
}
```


```{r fig.width=15, fig.height=8}
age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Urawa Red Diamonds",
                    color_1 = "black", color_2 = "red")
```




```{r fig.width=15, fig.height=8}
age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Sagan Tosu",
                    color_1 = "pink", color_2 = "lightblue")
```


```{r fig.width=15, fig.height=8}
age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Oita Trinita",
                    color_1 = "blue", color_2 = "yellow")
```


```{r fig.width=15, fig.height=8}
age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Gamba Osaka",
                    color_1 = "blue", color_2 = "black")
```





```{r fig.width=15, fig.height=8}
age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Cerezo Osaka",
                    color_1 = "violet", color_2 = "black")
```


```{r fig.width=15, fig.height=8}
age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Nagoya Grampus",
                    color_1 = "red", color_2 = "orange")
```

# Kawasaki Frontale

```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Kawasaki Frontale",
                    color_1 = "black", color_2 = "#1EB8FF",
                    j_name = "川崎フロンターレ",
                    img_path = here::here("img/KawasakiFrontale.png"))

combined_plot
```

Last season most of #Frontale's minutes were taken up by an aging core + rotating parts by a large # of players in their "peak" ages (a lot to cover for RB). Offseason, they've bought Issaka & Kamiya to provide more youthful backup. #川崎フロンターレ #JLeague

Getting Yamane from Shonan Bellmare will also help with solving the uncertainty around RB from last season. While the likes to Mitoma, Hatate, & Miyadai will hope to gain some minutes as cover for the veterans Damiao & Kobayashi.


```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/kawasakifrontale_combplot.png",
       height = 8, width = 15)
```



# FC Tokyo

```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = tokyo_minutes, 
                    team_name = "FC Tokyo",
                    color_1 = "#271672", color_2 = "#DD2220",
                    j_name = "FC 東京",
                    img_path = here::here("img/FCTokyo.png"))

combined_plot
```

```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/FCTokyo_combplot.png",
       height = 8, width = 15)
```


 #FCTokyo's title challenge came from a strong core of veteran players with squad roles mainly given to youth + Omori, Jang, Oh, & Mita. With a formation change & the transfer of Adailton & Leandro #FC東京 will have hopes for a first #JLeague title. #rstats #ggplot2 #SpoAna



# Kashima Antlers

```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Kashima Antlers",
                    color_1 = "darkred", color_2 = "black",
                    j_name = "鹿島アントラーズ",
                    img_path = here::here("img/Kashima_Antlers.png"))

combined_plot
```

```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/KashimaAntlers_combplot.png",
       height = 8, width = 15)
```

# Vissel Kobe

```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Vissel Kobe",
                    color_1 = "#bf0000", color_2 = "#000000",
                    j_name = "ヴィッセル神戸",
                    img_path = here::here("img/VisselKobe.png"))

combined_plot
```

```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/VisselKobe_combplot.png",
       height = 8, width = 15)
```


# Oita Trinita

```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Oita Trinita",
                    j_name = "大分トリニータ",
                    color_1 = "blue", color_2 = "#CCCC00",
                    img_path = here::here("img/OitaTrinita.png"))

combined_plot
```


```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/OitaTrinita_combplot.png",
       height = 8, width = 15)
```

# Gamba Osaka

```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Gamba Osaka",
                    j_name = "ガンバ大阪",
                    color_1 = "#10308E", color_2 = "black",
                    img_path = here::here("img/GambaOsaka.png"))

combined_plot
```


```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/GambaOsaka_combplot.png",
       height = 8, width = 15)
```

# Cerezo Osaka

```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Cerezo Osaka",
                    j_name = "セレッソ大阪",
                    color_1 = "#F1258E", color_2 = "#1C2581",
                    img_path = here::here("img/CerezoOsaka.png"))

combined_plot
```


```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/CerezoOsaka_combplot.png",
       height = 8, width = 15)
```


# Nagoya Gramps 8

```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Nagoya Grampus",
                    j_name = "名古屋グランパス",
                    color_1 = "red", color_2 = "orange",
                    img_path = here::here("img/NagoyaGrampus8.png"))

combined_plot
```


```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/NagoyaGrampus_combplot.png",
       height = 8, width = 15)
```



# Shimizu S-Pulse


```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Shimizu S-Pulse",
                    j_name = "清水エスパルス",
                    color_1 = "#F29900", color_2 = "#0569AE",
                    img_path = here::here("img/ShimizuSPulse.png"))

combined_plot
```


```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/ShimizuSPulse_combplot.png",
       height = 8, width = 15)
```



# Yokohama F. Marinos


```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Yokohama F. Marinos",
                    j_name = "横浜F・マリノス",
                    color_1 = "#003f99", color_2 = "#F40041",
                    img_path = here::here("img/YokohamaFMarinos.png"))

combined_plot
```


```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/YokohamaFMarinos_combplot.png",
       height = 8, width = 15)
```

# Shonan Bellmare


```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Shonan Bellmare",
                    j_name = "湘南ベルマーレ",
                    color_1 = "#67B356", color_2 = "#103C95",
                    img_path = here::here("img/ShonanBellmare.png"))

combined_plot
```


```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/ShonanBellmare_combplot.png",
       height = 8, width = 15)
```

# Urawa Red Diamonds


```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Urawa Red Diamonds",
                    j_name = "浦和レッドダイヤモンズ",
                    color_1 = "black", color_2 = "red",
                    img_path = here::here("img/UrawaReds.png"))

combined_plot
```


```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/UrawaReds_combplot.png",
       height = 8, width = 15)
```


# Sanfrecce Hiroshima

```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Sanfrecce Hiroshima",
                    j_name = "サンフレッチェ広島",
                    color_1 = "#533097", color_2 = "#AF9271",
                    img_path = here::here("img/SanfrecceHiroshima.png"))

combined_plot
```


```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/SanfrecceHiroshima_combplot.png",
       height = 8, width = 15)
```




# Hokkaido Consadole

```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Consadole Sapporo",
                    j_name = "北海道コンサドーレ札幌",
                    color_1 = "#0C506C", color_2 = "red",
                    img_path = here::here("img/ConsadoleSapporo.png"))

combined_plot
```


```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/ConsadoleSapporo_combplot.png",
       height = 8, width = 15)
```


# Vegalta Sendai

```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Vegalta Sendai",
                    j_name = "ベガルタ仙台",
                    color_1 = "#FDBE02", color_2 = "#DD030A",
                    img_path = here::here("img/VegaltaSendai.png"))

combined_plot
```


```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/VegaltaSendai_combplot.png",
       height = 8, width = 15)
```


# Matsumoto Yamaga

```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = yamaga_minutes, 
                    team_name = "Matsumoto Yamaga",
                    j_name = "松本山雅フットボールクラブ",
                    color_1 = "#005220", color_2 = "#016830",
                    img_path = here::here("img/MatsumotoYamaga.png"))

combined_plot
```


```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/MatsumotoYamaga_combplot.png",
       height = 8, width = 15)
```

# Jubilo Iwata

```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = jubilo_minutes, 
                    team_name = "Jubilo Iwata",
                    j_name = "ジュビロ磐田",
                    color_1 = "#5693c1", color_2 = "#000000",
                    img_path = here::here("img/JubiloIwata.png"))

combined_plot
```


```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/JubiloIwata_combplot.png",
       height = 8, width = 15)
```

# Sagan Tosu

```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = jleague_age_utility_df, 
                    team_name = "Sagan Tosu",
                    j_name = "サガン鳥栖",
                    color_1 = "#ec518f", color_2 = "#009acb",
                    img_path = here::here("img/SaganTosu.png"))

combined_plot
```


```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/SaganTosu_combplot.png",
       height = 8, width = 15)
```


# Kashiwa Reysol

```{r fig.width=15, fig.height=8}
combined_plot <- age_utility_plotter(df = reysol_minutes, 
                    team_name = "Kashiwa Reysol",
                    j_name = "柏レイソル",
                    color_1 = "#CCCC00", color_2 = "#000000",
                    img_path = here::here("img/KashiwaReysol.png"))

combined_plot
```


```{r}
ggsave(plot = combined_plot, "../J-League 2020/output/KashiwaReysol_combplot.png",
       height = 8, width = 15)
```













