---
title: "Untitled"
author: "RN7"
date: "December 26, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r message=FALSE}
pacman::p_load(tidyverse, scales, lubridate, ggrepel, stringi, magick, gapminder,
               glue, extrafont, rvest, ggtextures, cowplot, countrycode, ggimage,
               polite)
# necessary for Roboto Condensed font
loadfonts()
```

# Top goal scorers

```{r}
ac_top_scorers <- data.frame(
  player = c("Ali Daei", "Ali Daei", "Ali Daei",
             "Lee Dong Gook", "Lee Dong Gook",
             "Naohiro Takahara", "Naohiro Takahara",
             "Jassem Al-Houwaidi", "Jassem Al-Houwaidi",
             "Younis Mahmoud", "Younis Mahmoud", "Younis Mahmoud", "Younis Mahmoud"),
  country = c("Iran", "Iran", "Iran",
              "South Korea", "South Korea",
              "Japan", "Japan",
              "Kuwait", "Kuwait",
              "Iraq", "Iraq", "Iraq", "Iraq"),
  tournament = c("1996", "2000", "2004",
                 "2000", "2004",
                 "2000", "2004",
                 "1996", "2000",
                 "2004", "2007", "2011", "2015"),
  goals = as.numeric(c(8, 3, 3,
            6, 4,
            5, 4,
            6, 2,
            1, 4, 1, 2)),
  total_goals = as.numeric(c(14, 14, 14,
            10, 10,
            9, 9,
            8, 8,
            8, 8, 8, 8))
)

# soccer ball images
# https://i.pinimg.com/originals/e7/d7/19/e7d7190f0b5b3abd4f6c17e2c7989ec3.jpg
# https://www.emoji.co.uk/files/microsoft-emojis/activity-windows10/8356-soccer-ball.png
ac_top_scorers <- ac_top_scorers %>% 
  mutate(image = case_when(
    tournament == "2004" ~ "http://football-balls.com/ball_files/2004-asian-cup-adidas-roteiro-official-match-ball.png",
    tournament == "2007" ~ "http://football-balls.com/ball_files/2007-asian-cup-mercurial-veloci-official-match-ball.png",
    tournament == "2011" ~ "http://football-balls.com/ball_files/2011-asian-cup-nike-total-90-tracer-official-match-ball.png",
    tournament == "2015" ~ "http://football-balls.com/ball_files/2015-asian-cup-nike-ordem-2-official-match-ball.png",
    TRUE ~ "https://www.emoji.co.uk/files/microsoft-emojis/activity-windows10/8356-soccer-ball.png")) %>% 
  mutate(country_code = country %>% 
           countrycode(., origin = "country.name", destination = "iso2c"))


ac_top_scorers %>% 
  gather(key = "player", value = "tournament")

ac_top_scorers %>% 
  distinct(player, .keep_all = TRUE)
```


```{r, fig.width=8, fig.height=6}
ac_top_graph <- ac_top_scorers %>% 
  distinct(player, .keep_all = TRUE) %>% 
  ggplot(aes(x = reorder(player, total_goals), y = total_goals,
             image = image)) +
  #ggimage::geom_emoji(aes(image = '26bd'), size = 0.06) +
  geom_isotype_col(img_width = grid::unit(1, "native"), img_height = NULL,
    ncol = NA, nrow = 1, hjust = 0, vjust = 0.5) +
  coord_flip() +
  #geom_flag(y = -1.5, aes(image = country_code), size = 0.1) +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12, 14),
                     expand = c(0, 0), 
                     limits = c(0, 15)) +
  #expand_limits(y = -2) +
  ggthemes::theme_solarized() +
  labs(title = "Top Scorers of the Asian Cup!",
       subtitle = "Most goals in a single tournament: 8 (Ali Daei, 1996)",
       y = "Number of Goals", x = NULL) +
  theme(text = element_text(family = "Roboto Condensed"),
        title = element_text(size = 18),
        subtitle = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks.y = element_blank())

# scale them differently as flag sizes are different...
pimage <- axis_canvas(ac_top_graph, axis = 'y') + 
  draw_image("https://upload.wikimedia.org/wikipedia/commons/c/ca/Flag_of_Iran.svg", 
             y = 13, scale = 1.5) +
  draw_image("https://upload.wikimedia.org/wikipedia/commons/0/09/Flag_of_South_Korea.svg", 
             y = 10, scale = 1.7) +
  draw_image("https://upload.wikimedia.org/wikipedia/en/9/9e/Flag_of_Japan.svg", 
             y = 7, scale = 1.7) +
  draw_image("https://upload.wikimedia.org/wikipedia/commons/f/f6/Flag_of_Iraq.svg", 
             y = 4, scale = 1.6) +
  draw_image("https://upload.wikimedia.org/wikipedia/commons/a/aa/Flag_of_Kuwait.svg", 
             y = 1, scale = 1.2)

# insert the image strip into the bar plot and draw  
ggdraw(insert_yaxis_grob(ac_top_graph, pimage, position = "left"))
```


```{r}
theme_void
ggthemes::theme_wsj
ggthemes::theme_solarized
```





# Goals scored per tournament

```{r}
wiki_url <- "https://en.wikipedia.org"
acup_url <- "https://en.wikipedia.org/wiki/AFC_Asian_Cup"

cup_links <- read_html(acup_url) %>% 
  html_nodes("br+ i a") %>% 
  html_attr("href") %>% 
  .[-17:-18]


acup_df <- cup_links %>% 
  as_data_frame() %>% 
  mutate(cup = str_remove(value, "\\/wiki\\/") %>% str_replace_all("_", " ")) %>% 
  rename(link = value)



goals_info <- function(x) {
  goal_info <- wiki_url %>% 
    html_session() %>% 
    jump_to(x) %>% 
    html_nodes(".vcalendar") %>% 
    html_table(header = FALSE) %>% 
    flatten_df() %>% 
    spread(key = X1, value = X2) %>% 
    select(`Goals scored`) %>% 
    mutate(`Goals scored` = str_remove_all(`Goals scored`, pattern = ".*\\(") %>% 
             str_extract_all("\\d+\\.*\\d*") %>% as.numeric)
}

team_num_info <- function(x) {
  team_num_info <- wiki_url %>% 
    html_session() %>% 
    jump_to(x) %>% 
    html_nodes(".vcalendar") %>% 
    html_table(header = FALSE) %>% 
    flatten_df() %>% 
    spread(key = X1, value = X2) %>% 
    select(`Teams`) %>% 
    mutate(`Teams` = as.numeric(`Teams`))
}

match_num_info <- function(x) {
  match_num_info <- wiki_url %>% 
    html_session() %>% 
    jump_to(x) %>% 
    html_nodes(".vcalendar") %>% 
    html_table(header = FALSE) %>% 
    flatten_df() %>% 
    spread(key = X1, value = X2) %>% 
    janitor::clean_names() %>% 
    select(matches_played) %>% 
    mutate(matches_played = as.numeric(matches_played))
}


# all together:
goals_data <- acup_df %>% 
  mutate(goals_per_game = map(acup_df$link, goals_info) %>% unlist,
         team_num = map(acup_df$link, team_num_info) %>% unlist,
         match_num = map(acup_df$link, match_num_info) %>% unlist)

```

```{r}
ac_goals_df <- goals_data %>% 
  mutate(label = cup %>% str_extract("[0-9]+") %>% str_replace("..", "'"),
         team_num = case_when(
           is.na(team_num) ~ 16,
           TRUE ~ team_num
         )) %>% 
  arrange(cup) %>% 
  mutate(label = factor(label, label),
         team_num = c(4, 4, 4, 5, 6, 6, 10, 10, 10, 8, 12, 12, 16, 16, 16, 16))
```


```{r}
ac_goals_df %>% 
  ggplot(aes(x = label, y = goals_per_game, group = 1)) +
  geom_line() +
  #geom_point() +
  scale_y_continuous(limits = c(NA, 5.35),
                     breaks = c(1.5, 2, 2.5, 3, 3.5, 4, 4.5)) +
  labs(x = "Tournament (Year)", y = "Goals per Game"#,
       # title = "Goals per Game throughout the Asian Cup.",
       # subtitle = "Odd dip throughout the 80s to early 90s..."
       ) +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed"),
        #title = element_text(size = 18),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10)) +
  annotate(geom = "label", x = "'56", y = 5.23, family = "Roboto Condensed",
           color = "black", #fill = "grey",
           label = "Total Number of Games Played:", hjust = 0) +
  annotate(geom = "text", x = "'60", y = 4.9, 
           label = "6", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 1, xend = 3, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'68", y = 4.9, 
           label = "10", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 3.8, xend = 4.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'72", y = 4.9, 
           label = "13", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 4.8, xend = 5.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'76", y = 4.9, 
           label = "10", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 5.8, xend = 6.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'84", y = 4.9, 
           label = "24", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 7, xend = 9, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'92", y = 4.9, 
           label = "16", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 9.8, xend = 10.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = 11.5, y = 4.9, 
           label = "26", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 11, xend = 12, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = 14.5, y = 4.9, 
           label = "32", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 13, xend = 16, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = 9, y = 4, family = "Roboto Condensed",
           label = glue("
                        Incredibly low amount of goals in Group B
                        (15 in 10 Games) and in Knock-Out Stages
                        (4 goals in 4, only one scored in normal time)")) +
  annotate(geom = "segment", x = 9, xend = 9, y = 1.6, yend = 3.6,
           color = "red") +
  ggimage::geom_emoji(aes(image = '26bd'), size = 0.03) 

ggsave(filename = paste0(here::here("Asian Cup 2019"), "/gpg_plot.png"))
plot <- image_read(paste0(here::here("Asian Cup 2019"), "/gpg_plot.png"))
```

## add logo

```{r}
logo_raw <- image_read("https://upload.wikimedia.org/wikipedia/en/a/ad/2019_afc_asian_cup_logo.png")

logo <- logo_raw %>% 
  image_scale("100") %>% 
  image_background("grey", flatten = TRUE) %>% 
  image_border("grey", "600x10") %>% 
  image_annotate(text = glue("Goals per Game throughout the Asian Cup"),
                 color = "white", size = 30, 
                 location = "+10+50", gravity = "northwest")

final_plot <- image_append(image_scale(c(logo, plot), "500"), stack = TRUE)

logo_proc <- logo_raw %>% image_scale("100")

# create blank canvas
a <- image_blank(width = 6, height = 0.8, color = "white")

# combine with logo and shit it to the left, to the left
b <- image_composite(image_scale(a, "x100"), image_scale(logo_proc, "x60"), 
                     offset = "+500+25")
logo_2 <- b %>% 
  image_annotate(text = glue("Goals per Game throughout the Asian Cup"),
                 color = "black", size = 18, font = "Roboto Condensed",
                 location = "+63+50", gravity = "northwest")

final2_plot <- image_append(image_scale(c(logo_2, plot), "500"), stack = TRUE)
final2_plot
image_write(final2_plot,
            paste0(here::here("Asian Cup 2019"), "/gpg_plot_final.png"))
```

- annotate number of matches played on top as strip
- fit avg goals per game per each sequence of # of matches >>> kinda like splines
- add AFC logo? top right corner
- put top scorer country as geom_point?
- soccer ball emoji as geom_point?
- patchwork to include top scoring countries + other additional info


## add logo 2.0

```{r}
ac_goals_df %>% 
  ggplot(aes(x = label, y = goals_per_game, group = 1)) +
  geom_line() +
  scale_y_continuous(limits = c(NA, 5.35),
                     breaks = c(1.5, 2, 2.5, 3, 3.5, 4, 4.5)) +
  labs(x = "Tournament (Year)", y = "Goals per Game",
       title = "Goals per Game throughout the Asian Cup.") +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed"),
        #title = element_text(size = 18),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10)) +
  annotate(geom = "label", x = "'56", y = 5.23, family = "Roboto Condensed",
           color = "black", 
           label = "Total Number of Games Played:", hjust = 0) +
  annotate(geom = "text", x = "'60", y = 4.9, 
           label = "6", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 1, xend = 3, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'68", y = 4.9, 
           label = "10", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 3.8, xend = 4.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'72", y = 4.9, 
           label = "13", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 4.8, xend = 5.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'76", y = 4.9, 
           label = "10", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 5.8, xend = 6.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'84", y = 4.9, 
           label = "24", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 7, xend = 9, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = "'92", y = 4.9, 
           label = "16", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 9.8, xend = 10.2, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = 11.5, y = 4.9, 
           label = "26", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 11, xend = 12, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = 14.5, y = 4.9, 
           label = "32", family = "Roboto Condensed") +
  annotate(geom = "segment", x = 13, xend = 16, y = 4.8, yend = 4.8) +
  annotate(geom = "text", x = 9, y = 4, family = "Roboto Condensed",
           label = glue("
                        Incredibly low amount of goals in Group B
                        (15 in 10 Games) and in Knock-Out Stages
                        (4 goals in 4, only one scored in normal time)")) +
  annotate(geom = "segment", x = 9, xend = 9, y = 1.6, yend = 3.6,
           color = "red") +
  ggimage::geom_emoji(aes(image = '26bd'), size = 0.03) 

ggsave(filename = paste0(here::here("Asian Cup 2019"), "/gpg_title_plot.png"))
plot <- image_read(paste0(here::here("Asian Cup 2019"), "/gpg_title_plot.png"))
```


```{r}
add_logo <- function(plot_path, logo_path, logo_position, logo_scale = 10){

    # Requires magick R Package https://github.com/ropensci/magick

    # Useful error message for logo position
    if (!logo_position %in% c("top right", "top left", "bottom right", "bottom left")) {
        stop("Error Message: Uh oh! Logo Position not recognized\n  Try: logo_positon = 'top left', 'top right', 'bottom left', or 'bottom right'")
    }

    # read in raw images
    plot <- magick::image_read(plot_path)
    logo_raw <- magick::image_read(logo_path)

    # get dimensions of plot for scaling
    plot_height <- magick::image_info(plot)$height
    plot_width <- magick::image_info(plot)$width

    # default scale to 1/10th width of plot
    # Can change with logo_scale
    logo <- magick::image_scale(logo_raw, as.character(plot_width/logo_scale))

    # Get width of logo
    logo_width <- magick::image_info(logo)$width
    logo_height <- magick::image_info(logo)$height

    # Set position of logo
    # Position starts at 0,0 at top left
    # Using 0.01 for 1% - aesthetic padding

    if (logo_position == "top right") {
        x_pos = plot_width - logo_width - 0.01 * plot_width
        y_pos = 0.01 * plot_height
    } else if (logo_position == "top left") {
        x_pos = 0.01 * plot_width
        y_pos = 0.01 * plot_height
    } else if (logo_position == "bottom right") {
        x_pos = plot_width - logo_width - 0.01 * plot_width
        y_pos = plot_height - logo_height - 0.01 * plot_height
    } else if (logo_position == "bottom left") {
        x_pos = 0.01 * plot_width
        y_pos = plot_height - logo_height - 0.01 * plot_height
    }

    # Compose the actual overlay
    magick::image_composite(plot, logo, offset = paste0("+", x_pos, "+", y_pos))

}
```



```{r}
add_logo(plot_path = "gpg_title_plot.png",
         logo_path = "https://upload.wikimedia.org/wikipedia/en/a/ad/2019_afc_asian_cup_logo.png",
         logo_position = "top right",
         logo_scale = 15) -> plot_2.0

plot_2.0
```






```{r}
wiki_url %>% 
  html_session() %>% 
  jump_to("/wiki/2015_AFC_Asian_Cup") %>% 
  html_nodes(".vcalendar") %>% 
  html_table(header = FALSE) %>% 
  flatten_df() %>% 
  spread(key = X1, value = X2) %>% 
  select(`Goals scored`) %>% 
  mutate(`Goals scored` = str_remove_all(`Goals scored`, pattern = ".*\\(") %>% 
           str_extract_all("\\d+\\.*\\d*") %>% as.numeric)
```


```{r}
###

one_cup <- "https://en.wikipedia.org/wiki/1968_AFC_Asian_Cup"

copa <- one_cup %>% 
  read_html() %>% 
  html_nodes(".vcalendar") %>% 
  html_table(header = FALSE) %>% 
  flatten_df() %>% 
  spread(key = X1, value = X2) %>% 
  janitor::clean_names() %>% 
  select(goals_scored) %>% 
  mutate(`Goals scored` = str_remove_all(`Goals scored`, pattern = ".*\\(") %>% 
           str_extract_all("\\d+\\.*\\d*") %>% as.numeric) # \\(.*)

```








# Asian Cup record

```{r}
# .navigation-not-searchable+ .jquery-tablesorter

acup_url <- "https://en.wikipedia.org/wiki/AFC_Asian_Cup"

session <- bow(acup_url)

acup_winners_raw <- scrape(session) %>% 
  html_nodes("#mw-content-text > div > table:nth-child(30)") %>% 
  html_table() %>% 
  flatten_df()
```

```{r}
acup_winners_clean <- acup_winners_raw %>% 
  janitor::clean_names() %>% 
  slice(1:8) %>% 
  select(-fourth_place, -total_top_four) %>% 
  separate(winners, into = c("first_num", "first_place_year"), sep = " ", extra = "merge") %>% 
  separate(runners_up, into = c("second_num", "second_place_year"), sep = " ", extra = "merge") %>% 
  separate(third_place, into = c("third_num", "third_place_year"), sep = " ", extra = "merge") %>% 
  mutate_all(funs(str_replace_all(., "–", "0"))) %>% 
  mutate_at(vars(contains("num")), funs(as.numeric)) %>% 
  mutate(team = if_else(team == "Israel1", "Israel", team)) %>% 
  gather(key = "key", value = "value", -team, 
         -first_place_year, -second_place_year, -third_place_year) %>% 
  mutate(key = case_when(
           key == "first_num" ~ "Champions",
           key == "second_num" ~ "Runners-up",
           key == "third_num" ~ "Third Place"
         ),
         key = key %>% fct_relevel(c("Champions", "Runners-up", "Third Place"))) %>% 
  # hack-ish solution?
  arrange(key, value) %>% 
  mutate(team = as_factor(team),
         order = row_number(),
         image = team %>% 
           countrycode(., origin = "country.name", destination = "iso2c"))
```

```{r, fig.width = 8, fig.height = 6}
a <- acup_winners_clean %>% 
  ggplot(aes(value, team, color = key)) +
  geom_point(size = 5) +
  scale_color_manual(values = c("Champions" = "#FFCC33",
                                "Runners-up" = "#999999",
                                "Third Place" = "#CC6600"),
                     guide = FALSE) +
  labs(x = "Number of Occurrence",
       title = "Winners & Losers of the Asian Cup (1956-2015)",
       subtitle = glue("
                       Ordered by number of Asian Cup(s) won.
                       Four-time Champions, Japan, only won their first in 1992!"),
       caption = glue("
                      Note: Israel was expelled by the AFC in 1974 while Australia joined the AFC in 2006.
                      Source: Wikipedia
                      By @R_by_Ryo")) +
  facet_wrap(~key) +
  theme_minimal() +
  theme(text = element_text(family = "Roboto Condensed"),
        title = element_text(size = 18),
        plot.subtitle = element_text(size = 12),
        axis.title.y = element_blank(),
        axis.title.x = element_text(size = 12),
        axis.text.y = element_text(size = 14),
        axis.text.x = element_text(size = 12),
        plot.caption = element_text(hjust = 0, size = 10),
        panel.border = element_rect(fill = NA, colour = "grey20"),
        panel.grid.minor.x = element_blank(),
        strip.text = element_text(size = 16))

ggsave("../Asian Cup 2019/asiancup_winners.png", width = 8, height = 6)

# a +
#   geom_flag(data = acup_winners_clean, 
#             x = -2, aes(image = image), size = 0.15) +
#   expand_limits(x = -2)

# insert_yaxis_grob()

#null_dev_env <- new.env(parent = emptyenv())
# set_null_device("pdf")
# cairo_pdf()
# ggdraw(add_sub(a, label = "Source: Wikipedia\nBy @R_by_Ryo", x = 0.95, size = 8))
# 
# Cairo::Cairo(1000, 750, "test.png", bg = "white")
# last_plot()
# dev.off()
```




# Working hours & Productivity

```{r}
acup_url <- "https://en.wikipedia.org/wiki/2019_AFC_Asian_Cup"

acup_kickoff <- acup_url %>% 
  read_html() %>% 
  html_nodes("time") %>% 
  html_text() %>% 
  as_data_frame()

# time
```

- calculate +90 minutes for entire game duration
- NOT count extra time or stoppage time
- cross-refernce with other local time zones
- count up total number of hours per each spectator country

```{r}
acup_kickoff %>% 
  mutate(match_num = row_number(),
         match_type = if_else(between(match_num, 37, 51), 
                              "Knock-Out Stage", "Group Stage"),
         time = value %>% str_replace("\\(.*\\)", "")) %>% 
  mutate(time2 = hm(time),
         time_ac2 = force_tz(time2, "Asia/Dubai"), # time based in UTC +4
         time_jp = with_tz(time_ac2, tz = "Asia/Tokyo"), # UTC +4 time converted to Japan
         time_jp_end = time_jp + hm("2 0"),
         time_ac = with_tz(time2, tz = "America/New_York"),
         timeZONE2 = tz(time_ac)) %>% 
  mutate(diff = make_difftime(hour = 2),
         int = as.interval(diff, time_ac2),
         jp_start = hm("09:00") %>% with_tz(tz = "Asia/Tokyo"),
         jp_end = hm("12:00") %>% with_tz(tz = "Asia/Tokyo"),
         jp_work = as.interval(jp_start, jp_end),
         overlap = int_overlaps(jp_work, int))


acup_kickoff %>% 
  mutate(match_num = row_number(),
         match_type = if_else(between(match_num, 37, 51), 
                              "Knock-Out Stage", "Group Stage"),
         time = value %>% str_replace("\\(.*\\)", "")) %>% 
  mutate(time2 = dmy_hm(time),
         time3 = hour(time2))
```



```{r}
#tz <- "Asia/"
acup_times_df <- acup_kickoff %>% 
  mutate(time = value %>% str_replace("\\(.*\\)", "")) %>% 
  mutate(time2 = dmy_hm(time)) %>%  # proper time var
  arrange(time2) %>% 
  mutate(
         # match num must arrangeDESC time2
         match_num = row_number(),
         match_type = if_else(between(match_num, 37, 51), 
                              "Knock-Out Stage", "Group Stage"),
         # 
         is_weekday = wday(time2, label = TRUE),
         time_ac2 = force_tz(time2, "Asia/Dubai"), # time based in UTC +4
         time_jp = with_tz(time_ac2, tz = "Asia/Tokyo"), # UTC +4 time converted to Japan
         time_jp_end = time_jp + hm("2 0"),
         time_ac = with_tz(time2, tz = "America/New_York")) %>% # UTC +4 time to NYC
  mutate(diff = make_difftime(hour = 2),
         int = as.interval(diff, time_ac2),
         # jp_start = ymd_hms("2019-01-05 09:00:00", tz = "Asia/Tokyo"),
         # jp_end = ymd_hms("2019-01-05 12:00:00", tz = "Asia/Tokyo"),
         jp_match = as.interval(time_jp, time_jp_end),
         overlap = int_overlaps(jp_match, int)) %>% 
  select(jp_match, int, overlap)

# now create 9AM-5PM for Japan for each of those days on the match days!!
# is_weekday? T/F

acup_times_df$jp_work %within% acup_times_df$int

```

ymd_hms("2011-07-01 09:00:00", tz = "Pacific/Auckland")




```{r}
acup_kickoff %>% 
  mutate(time = value %>% str_replace("\\(.*\\)", "")) %>% 
  mutate(time2 = dmy_hm(time)) %>%  # proper time var
  arrange(time2) %>% 
  mutate(match_num = row_number(),
         match_type = if_else(between(match_num, 37, 51), 
                              "Knock-Out Stage", "Group Stage"),
         # 
         is_weekday = wday(time2, label = TRUE),
         time_ac2 = force_tz(time2, "Asia/Dubai"), # time based in UTC +4
         time_ny = with_tz(time_ac2, tz = "America/New_York"), # converted to NYC
         time_ny_end = time_ny + hm("2 0")) %>% 
  mutate(work_time = time %>% str_sub(end = -6),
         work_time_begin = glue("{work_time} 09:00") %>% 
           dmy_hm(tz = "America/New_York"),
         work_time_end = glue("{work_time} 17:00") %>% 
           dmy_hm(tz = "America/New_York")) %>% 
  # create intervals
  mutate(diff = make_difftime(hour = 2),
         int = as.interval(diff, time_ac2),
         int_ny_work = as.interval(work_time_begin, work_time_end),
         ny_match = as.interval(time_ny, time_ny_end),
         overlap = int_overlaps(ny_match, int_ny_work)) %>% 
  # sum overlapping hours?
  mutate(overlap_num = pmax(pmin(time_ny_end, work_time_end) - 
                              pmax(time_ny, work_time_begin) + 1,0)) %>% 
  mutate(overlap_laplap = map2_dbl(work_time_begin, work_time_end,
                                   ~pmax((pmin(time_ny_end, .y)) - 
                                          pmax(time_ny, .x) + 1), 0)) %>% 
  select(ny_match, int, overlap, overlap_num, overlap_laplap)
```


## NY time

```{r}
acup_kickoff %>% 
  mutate(time = value %>% str_replace("\\(.*\\)", "")) %>% 
  mutate(time2 = dmy_hm(time)) %>%  # proper time var
  arrange(time2) %>% 
  mutate(match_num = row_number(),
         match_type = if_else(between(match_num, 37, 51), 
                              "Knock-Out Stage", "Group Stage"),
         # 
         is_weekday = wday(time2, label = TRUE),
         time_ac2 = force_tz(time2, "Asia/Dubai"), # time based in UTC +4
         time_jp = with_tz(time_ac2, tz = "Asia/Tokyo"), # UTC +4 time converted to Japan
         time_jp_end = time_jp + hm("2 0")) %>% 
  mutate(work_time = time %>% str_sub(end = -6),
         work_time_begin = glue("{work_time} 09:00") %>% 
           dmy_hm(tz = "Asia/Tokyo"),
         work_time_end = glue("{work_time} 17:00") %>% 
           dmy_hm(tz = "Asia/Tokyo")) %>% 
  # create intervals
  mutate(diff = make_difftime(hour = 2),
         int = as.interval(diff, time_ac2),
         int_jp_work = as.interval(work_time_begin, work_time_end),
         jp_match = as.interval(time_jp, time_jp_end),
         overlap = int_overlaps(jp_match, int_jp_work)) %>% 
  select(jp_match, int, overlap)
```


# Japan vs. RIVALS

- use Kaggle international results
- results UP TO END OF WORLD CUP
- filter AFC Asian Cup, Friendly, AFC Asian Cup qualification
- filter Asia >>> take out UEFA countries like Kazakhstan, Georgia, Israel, etc.


- https://www.kaggle.com/phjulien/a-journey-through-the-history-of-soccer/

```{r}
federation_files <- Sys.glob("../data/federation_affiliations/*")

df_federations = data.frame(country = NULL, federation = NULL)
for (f in federation_files) {
    federation = basename(f)
    content = read.csv(f, header=FALSE)
    content <- cbind(content,federation=rep(federation, dim(content)[1]))
    df_federations <- rbind(df_federations, content)
}

colnames(df_federations) <- c("country", "federation")

df_federations <- df_federations %>% 
  mutate(country = as.character(country) %>% str_trim(side = "both"))
```

```{r}
results_raw <- read_csv("../data/results.csv")

results_japan_raw <- results_raw %>% 
  filter(home_team == "Japan" | away_team == "Japan") %>% 
  rename(venue_country = country, 
         venue_city = city) %>% 
  mutate(match_num = row_number())

# combine with federation affiliations
results_japan_home <- results_japan_raw %>% 
  left_join(df_federations, 
            by = c("home_team" = "country")) %>% 
  mutate(federation = as.character(federation)) %>% 
  rename(home_federation = federation) #%>% 
  View()

results_japan_away <- results_japan_raw %>% 
  left_join(df_federations, 
            by = c("away_team" = "country")) %>% 
  mutate(federation = as.character(federation)) %>% 
  rename(away_federation = federation) #%>% 
  View()

# combine home-away
results_japan_cleaned <- results_japan_home %>% 
  full_join(results_japan_away)

results_japan_cleaned %>% 
  filter(is.na(home_federation)) %>% 
  pull(home_team) %>% 
  unique()

results_japan_cleaned %>% 
  filter(is.na(away_federation)) %>% 
  pull(away_team) %>% 
  unique()

```



```{r}
results_japan_cleaned <- results_japan_cleaned %>% 
  mutate(
    home_federation = case_when(
      home_team %in% c(
        "China", "Manchukuo", "Burma", "Korea Republic", "Vietnam Republic",
        "Korea DPR", "Brunei") ~ "AFC",
      home_team == "USA" ~ "Concacaf",
      home_team == "Bosnia-Herzegovina" ~ "UEFA",
      TRUE ~ home_federation),
    away_federation = case_when(
      away_team %in% c(
        "China", "Manchukuo", "Burma", "Korea Republic", "Vietnam Republic",
        "Korea DPR", "Brunei", "Taiwan") ~ "AFC",
      away_team == "USA" ~ "Concacaf",
      away_team == "Bosnia-Herzegovina" ~ "UEFA",
      TRUE ~ away_federation
    ))
```

Now that it's nice and cleaned up I can reshape it so that the data is set from Japan's perspective.

```{r}
# reshape to Japan p.o.v.

results_jp_asia <- results_japan_cleaned %>% 
  # filter only for Japan games and AFC opponents
  filter(home_team == "Japan" | away_team == "Japan",
         home_federation == "AFC" & away_federation == "AFC") %>% 
  select(-contains("federation"), -contains("venue"),
         -neutral, -match_num,
         date, home_team, home_score, away_team, away_score, tournament) %>% 
  # reshape columns to Japan vs. opponent
  mutate(
    opponent = case_when(
      away_team != "Japan" ~ away_team,
      home_team != "Japan" ~ home_team),
    home_away = case_when(
      home_team == "Japan" ~ "home",
      away_team == "Japan" ~ "away"),
    japan_goals = case_when(
      home_team == "Japan" ~ home_score,
      away_team == "Japan" ~ away_score),
    opp_goals = case_when(
      home_team != "Japan" ~ home_score,
      away_team != "Japan" ~ away_score)) %>% 
  # results
  mutate(
    result = case_when(
      japan_goals > opp_goals ~ "Win",
      japan_goals < opp_goals ~ "Loss",
      japan_goals == opp_goals ~ "Draw"),
    result = result %>% as_factor() %>% fct_relevel(c("Win", "Draw", "Loss"))) %>% 
  select(-contains("score"), -contains("team"))


#results_jp_asia %>% View()
```



```{r}
results_jp_asia %>% 
  filter(opponent == "Uzbekistan") %>% 
  group_by(result) %>% 
  count()

results_jp_asia %>% 
  filter(opponent == "Turkmenistan")

results_jp_asia %>% 
  filter(opponent == "Oman") %>% 
  knitr::kable()


results_jp_asia %>% 
  filter(opponent %in% c("Oman", "Uzbekistan", "Turkmenistan")) %>% 
  group_by(result, opponent) %>% 
  tally()

results_jp_asia %>% 
  filter(opponent %in% c("Oman", "Uzbekistan", "Turkmenistan")) %>% 
  group_by(result, opponent) %>% 
  summarize(j_g = sum(japan_goals),
            o_g = sum(opp_goals),
            n = n()) %>% 
  spread(result, n)
```



```{r}
results_jp_asia %>% 
  filter(opponent %in% c("Australia", "Korea Republic", "Iran")) %>% 
  group_by(result, opponent) %>% 
  mutate(n = n()) %>% 
  ungroup() %>% 
  group_by(result, opponent) %>% 
  summarize(j_g = sum(sum(japan_goals)),
            o_g = sum(sum(opp_goals)),
            n = n()) %>% 
  ungroup() %>% 
  spread(result, n) %>% 
  group_by(opponent) %>% 
  mutate(j_g = sum(j_g),
         o_g = sum(o_g),
         Win = sum(Win, na.rm = TRUE),
         Draw = sum(Draw, na.rm = TRUE),
         Loss = sum(Loss, na.rm = TRUE)) %>% 
  distinct()

```

thankfull south korea should be on the otherside of the bracket and we would also only meet Iran in the semifinals

Japan could meet Australia in the Quarters but without Aaron Mooy they're a much weaker side

Japan have unfortunately lost our rising star, Nakajima, to injury but we have replaced him with World Cup hero Takashi Inui.

```{r, echo=FALSE}
results_jp_asia %>% 
  filter(opponent %in% c("Oman", "Vietnam", "India")) %>% 
  group_by(result, opponent) %>% 
  mutate(n = n()) %>% 
  ungroup() %>% 
  group_by(home_away, result, opponent) %>% 
  summarize(j_goals = sum(japan_goals),
         oppo_goals = sum(opp_goals),
         n = n()) %>% 
  ungroup() %>% 
  arrange(opponent, result) %>% 
  spread(result, n) %>% 
  group_by(opponent, home_away) %>% 
  mutate(Win = if("Win" %in% names(.)){return(Win)} else{return(0)},
         Draw = if("Draw" %in% names(.)){return(Draw)} else{return(0)},
         Loss = if("Loss" %in% names(.)){return(Loss)} else{return(0)}) %>% 
  summarize(Win = sum(Win, na.rm = TRUE),
         Draw = sum(Draw, na.rm = TRUE),
         Loss = sum(Loss, na.rm = TRUE),
         j_goals = sum(j_goals),
         o_goals = sum(oppo_goals)) %>% 
  ungroup() %>% 
  group_by(opponent) %>% 
  do(add_row(.,
             opponent = .$opponent %>% unique(),
             home_away = "total",
             Win = sum(.$Win, na.rm = TRUE),
             Draw = sum(.$Draw, na.rm = TRUE),
             Loss = sum(.$Loss, na.rm = TRUE),
             j_goals = sum(.$j_goals),
             o_goals = sum(.$o_goals)))
```



# waffle charts

```{r}
library(waffle)

tibble(
  team = c("Liverpool FC", "Draw", "Man. Utd"),
  values = c(55, 46, 68)
) -> liv_man

cols <- c("Liverpool FC" = "red", 
          "Draw" = "grey",
          "Man. Utd" = "black")

liv_man %>% 
  mutate(team = as_factor(team) %>% fct_relevel("Liverpool FC", "Draw", "Man. Utd")) %>% 
  ggplot(aes(fill = team, values = values)) +
  geom_waffle(color = "white", size = 1.125, n_rows = 6) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  scale_fill_manual(values = cols, name = NULL) +
  #ggthemes::scale_fill_tableau(name=NULL) +
  coord_equal() +
  hrbrthemes::theme_ipsum_rc(grid = "") +
  theme_enhance_waffle() +
  labs(title = "The North West Derby")
```


## japan_versus function

```{r}
japan_versus <- function(data, ...) {
  # filter 
  filter_vars <- enquos(...)
  
  jp_vs <- data %>% 
    filter(!!!filter_vars) %>% 
    # count results type per opponent
    group_by(result, opponent) %>% 
    mutate(n = n()) %>% 
    ungroup() %>% 
    # sum amount of goals by Japan and opponent
    group_by(result, opponent) %>% 
    summarize(j_g = sum(japan_goals),
              o_g = sum(opp_goals),
              n = n()) %>% 
    ungroup() %>% 
    # spread results over multiple columns
    spread(result, n) %>% 
    # 1. failsafe against no type of result against an opponent
    # 2. sum up counts per opponent
    group_by(opponent) %>% 
    mutate(Win = if("Win" %in% names(.)){return(Win)} else{return(0)},
         Draw = if("Draw" %in% names(.)){return(Draw)} else{return(0)},
         Loss = if("Loss" %in% names(.)){return(Loss)} else{return(0)}) %>% 
    summarize(Win = sum(Win, na.rm = TRUE),
              Draw = sum(Draw, na.rm = TRUE),
              Loss = sum(Loss, na.rm = TRUE),
              `Goals For` = sum(j_g),
              `Goals Against` = sum(o_g))
  
  return(jp_vs)
}
```

```{r, fig.height = 4, fig.width=3}
library(waffle)
library(extrafont)
loadfonts(device = "win")

results_jp_asia <- readRDS("../data/results_jp_asia.RDS")

glimpse(results_jp_asia)

jp_aus <- results_jp_asia %>% 
  japan_versus(opponent == "Australia") %>% 
  select(-opponent, Japan = Win, Australia = Loss) %>% 
  gather(key = "team", value = "values", -`Goals For`, -`Goals Against`) %>% 
  select(-contains("Goals"))

waffle(
  jp_aus, rows = 4, size = 1, 
  title = glue("
               Japan vs. Australia: 
               The New 'Asian' Rivalry"),
  colors = c("red", "grey", "blue"), 
  use_glyph = "futbol", glyph_size = 5,
  legend_pos = "bottom"
)

```



```{r}
pal <- c("Japan" = "blue", "Draw" = "grey", "South Korea" = "red")

results_jp_asia %>% 
  japan_versus(opponent == "Korea Republic") %>% 
  select(-opponent, Japan = Win, `South Korea` = Loss) %>% 
  gather(key = "team", value = "values", -`Goals For`, -`Goals Against`) %>% 
  ggplot(aes(fill = team, values = values)) +
  geom_waffle(color = "white", size = 1.125, n_rows = 6) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  scale_fill_manual(values = pal, name = NULL) +
  coord_equal() +
  hrbrthemes::theme_ipsum_rc(grid="") +
  theme_enhance_waffle() +
  labs(title = "Japan vs. South Korea")

```



## time between start-finish + distance travelled

bar plot + calendar plot