---
title: "Untitled"
author: "RN7"
date: "January 12, 2019"
output: 
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

A new rival, Australia, emerged to challenge Japan in Asia as they joined the AFC in 2006. From the come-from-behind defeat in the Group Stages of the 2006 World Cup (still one of my most painful memories as a Japanese football fan...) and to an extra-time win in the 2011 Asian Cup Final, Japan and Australia have dramatically clashed in the past decade.

Using the `waffle` package I can create a graphic that summarizes the results between the two sides.


```{r}
japan_versus <- function(data, ...) {
  # filter 
  filter_vars <- enquos(...)
  
  jp_vs <- data %>% 
    filter(!!!filter_vars) %>% 
    # count results type per opponent
    group_by(result, opponent) %>% 
    mutate(n = n()) %>% 
    ungroup() %>% 
    # sum amount of goals by Japan and opponent
    group_by(result, opponent) %>% 
    summarize(j_g = sum(japan_goals),
              o_g = sum(opp_goals),
              n = n()) %>% 
    ungroup() %>% 
    # spread results over multiple columns
    spread(result, n) %>% 
    # 1. failsafe against no type of result against an opponent
    # 2. sum up counts per opponent
    group_by(opponent) %>% 
    mutate(Win = if("Win" %in% names(.)){return(Win)} else{return(0)},
         Draw = if("Draw" %in% names(.)){return(Draw)} else{return(0)},
         Loss = if("Loss" %in% names(.)){return(Loss)} else{return(0)}) %>% 
    summarize(Win = sum(Win, na.rm = TRUE),
              Draw = sum(Draw, na.rm = TRUE),
              Loss = sum(Loss, na.rm = TRUE),
              `Goals For` = sum(j_g),
              `Goals Against` = sum(o_g))
  
  return(jp_vs)
}
```

```{r, fig.height = 4, fig.width=3}
library(glue)
library(dplyr)
library(tidyr)
library(waffle)
library(extrafont)
loadfonts(device = "win")

results_jp_asia <- readRDS("../data/results_jp_asia.RDS")


jp_aus <- results_jp_asia %>% 
  japan_versus(opponent == "Australia") %>% 
  select(-opponent, Japan = Win, Australia = Loss) %>% 
  gather(key = "team", value = "values", -`Goals For`, -`Goals Against`) %>% 
  select(-contains("Goals"))

# Waffle plot!
waffle(
  jp_aus, rows = 4, size = 1, 
  title = glue("
               Japan vs. Australia: 
               The New 'Asian' Rivalry"),
  colors = c("red", "grey", "blue"), 
  use_glyph = "futbol", glyph_size = 5,
  legend_pos = "bottom"
)

```

