---
title: "Untitled"
author: "RN7"
date: "March 9, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# MAIN QUESTIONS
- is squad reaching its peak years?
- how much youth is used by teams?
- changes/trends over seasons? overall transfer strategies? (highlight NEW players on plot?)


# R related problems

- how to scale up?
-- instead of copy-paste same code, can use purrr BUT each team needs some manual fixing of names and other small little edits ...
- create function that only needs new team {name}, and insert {primay color} and {secondary color}
-- this can be easily done... 
- introduce semi-transparent grey lines at 50% and Age == 25??

# Packages
```{r, message=FALSE, warning=FALSE}
pacman::p_load(tidyverse, polite, scales, ggimage, rvest, 
               glue, extrafont, ggrepel, magick, ggforce)
loadfonts()
```

# functions

## add_logo functions

```{r}
add_logo <- function(plot_path, logo_path, logo_position, logo_scale = 10){

    # Requires magick R Package https://github.com/ropensci/magick

    # Useful error message for logo position
    if (!logo_position %in% c("top right", "top left", "bottom right", "bottom left")) {
        stop("Error Message: Uh oh! Logo Position not recognized\n  Try: logo_positon = 'top left', 'top right', 'bottom left', or 'bottom right'")
    }

    # read in raw images
    plot <- magick::image_read(plot_path)
    logo_raw <- magick::image_read(logo_path)

    # get dimensions of plot for scaling
    plot_height <- magick::image_info(plot)$height
    plot_width <- magick::image_info(plot)$width

    # default scale to 1/10th width of plot
    # Can change with logo_scale
    logo <- magick::image_scale(logo_raw, as.character(plot_width/logo_scale))

    # Get width of logo
    logo_width <- magick::image_info(logo)$width
    logo_height <- magick::image_info(logo)$height

    # Set position of logo
    # Position starts at 0,0 at top left
    # Using 0.01 for 1% - aesthetic padding

    if (logo_position == "top right") {
        x_pos = plot_width - logo_width - 0.01 * plot_width
        y_pos = 0.01 * plot_height
    } else if (logo_position == "top left") {
        x_pos = 0.01 * plot_width
        y_pos = 0.01 * plot_height
    } else if (logo_position == "bottom right") {
        x_pos = plot_width - logo_width - 0.01 * plot_width
        y_pos = plot_height - logo_height - 0.01 * plot_height
    } else if (logo_position == "bottom left") {
        x_pos = 0.01 * plot_width
        y_pos = plot_height - logo_height - 0.01 * plot_height
    }

    # Compose the actual overlay
    magick::image_composite(plot, logo, offset = paste0("+", x_pos, "+", y_pos))

}
```

## tategaki function

```{r}
tategaki <- function(x){
  x <- chartr("ー", "丨", x) # 長音符の処理
  x <- strsplit(split="", x)
  sapply(x, paste, collapse="\n")
}

tategaki_alt <- function(x){
  x <- stringr::str_replace_all(x, "ー", "丨") # 長音符の処理
  stringr::str_wrap(x, width = 1)
}
```


# Vissel Kobe

## scrape
```{r}
session <- bow("https://www.transfermarkt.com/vissel-kobe/leistungsdaten/verein/3958/plus/0?reldata=JAP1%262017")

print(session)
# "The path is scrapable for this user-agent": OK, looks like we are good to go!

# scraping tranfermarkt is a nightmare...
# scrape each col individually then combine later...

# grab name from photo element instead
result_name <- scrape(session) %>% 
  html_nodes("#yw1 .bilderrahmen-fixed") %>% 
  html_attr("title") 

# grab age
result_age <- scrape(session) %>% 
  html_nodes(".posrela+ .zentriert") %>% 
  html_text()

# grab minutes played in league
result_mins <- scrape(session) %>% 
  html_nodes("td.rechts") %>% 
  html_text()
```

## clean

```{r}
# place each vector into list

resultados <- list(result_name, result_age, result_mins)

col_name <- c("name", "age", "minutes")

# then reduce(cbind) to combine them, set names to cols 
resultados %>% 
  reduce(cbind) %>% 
  as_tibble() %>% 
  set_names(col_name) -> results_comb

# NOICE.gif
glimpse(results_comb)

# fix "strings" into proper formats, calculate % of minutes appeared
kobe_minutes <- results_comb %>% 
  
  mutate(age = as.numeric(age),
         minutes = minutes %>% 
           str_replace("\\.", "") %>% 
           str_replace("'", "") %>% 
           as.numeric(),
         min_perc = (minutes / 3060) %>% round(digits = 3)) %>% 
  
  filter(!is.na(minutes)) %>% 
  
  separate(name, into = c("first_name", "last_name"), by = " ") %>%
  # manually fix somes names
  mutate(last_name = case_when(
    first_name == "Wellington" ~ "Wellington", 
    first_name == "Seung" ~ "S.G. Kim",
    first_name == "Leandro" ~ "Leandro",
    first_name == "Woo" ~ "W.Y. Jung",
    TRUE ~ last_name
  )) %>% 
  
  arrange(desc(min_perc))

# rectanglular highlight for players in their prime:
rect_df <- data.frame(
  xmin = 26, xmax = 31,
  ymin = -Inf, ymax = Inf
)

glimpse(kobe_minutes)
```



## plot

```{r fig.height=6, fig.width=8}
kobe_minutes %>% 
  ggplot(aes(x = age, y = min_perc)) +
  geom_vline(xintercept = 25, alpha = 0.4, color = "grey20") +
  geom_hline(yintercept = 0.5, alpha = 0.4, color = "grey20") +
  geom_mark_rect(aes(filter = age >= 26 & age <= 31), 
                 description = "ピーク年齢*", con.cap = 0,
                 color = NA,　fill = "firebrick1", alpha = 0.5) + 
  #geom_point(color = "firebrick1", size = 2.5) +
  geom_point(color = "darkred", size = 2.5) +
  geom_text_repel(
    aes(label = last_name, family = "Roboto Condensed"),
    nudge_x = 0.5,
    seed = 6) + 
  scale_y_continuous(
    expand = c(0.01, 0),
    limits = c(0, 1), 
    labels = percent_format()) +
  scale_x_continuous(
    breaks = pretty_breaks(n = 10)) +
  labs(
    x = "年齢", 
    y = tategaki_alt("出場時間（％）"),  
    title = "ヴィッセル神戸: 年齢-出場時間プロット",
    subtitle = "J-League 2018 Season (100% = 3060分)",
    caption = glue("
                   データ: transfermarkt.com
                   *主観
                   作: @R_by_Ryo"))  +
  theme_bw() +
  theme(
    text = element_text(family = "Roboto Condensed"),
    plot.title = element_text(color = "darkred", size = 16, face = "bold"),
    plot.subtitle = element_text(size = 14),
    axis.title.y = element_text(angle = 0, vjust= 0.5),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    panel.border = element_rect(color = "darkred", size = 1.25)) -> kobe_plot
```

```{r}
ggsave(plot = kobe_plot, "../J-League 2018/output/kobe_plot.png",
       height = 6, width = 8)
```



```{r}
plot_logo <- add_logo(plot_path = "../J-League 2018/output/kobe_plot.png",
                      logo_path = "https://upload.wikimedia.org/wikipedia/en/8/87/VisselKobe.png",
                      logo_position = "top right",
                      logo_scale = 20)

plot_logo
```

```{r}
image_write(image = plot_logo, "../J-League 2018/output/kobe_logo_plot.png")
```

### english version

```{r fig.height=6, fig.width=8}
kobe_minutes %>% 
  ggplot(aes(x = age, y = min_perc)) +
  geom_vline(xintercept = 25, alpha = 0.4, color = "grey20") +
  geom_hline(yintercept = 0.5, alpha = 0.4, color = "grey20") +
  geom_mark_rect(aes(filter = age >= 26 & age <= 31), 
                 description = "Prime Age*", con.cap = 0,
                 color = NA,　fill = "firebrick1", alpha = 0.5) + 
  geom_point(color = "darkred", size = 2.5) +
  geom_text_repel(
    aes(label = last_name, family = "Roboto Condensed"),
    nudge_x = 0.5,
    seed = 6) + 
  scale_y_continuous(
    expand = c(0.01, 0),
    limits = c(0, 1), 
    labels = percent_format()) +
  scale_x_continuous(
    breaks = pretty_breaks(n = 10)) +
  labs(
    x = "Current Age (As of March 30, 2019)", 
    y = "% of Minutes Played",  
    title = "Vissel Kobe: Age-Utility Matrix",
    subtitle = "J-League 2018 Season (100% = 3060 minutes)",
    caption = glue("
                   Data: transfermarkt.com
                   *Subjective
                   Created by: @R_by_Ryo"))  +
  theme_bw() +
  theme(
    text = element_text(family = "Roboto Condensed"),
    plot.title = element_text(color = "darkred", size = 16, face = "bold"),
    plot.subtitle = element_text(size = 14),
    #axis.title.y = element_text(angle = 0, vjust= 0.5),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    panel.border = element_rect(color = "darkred", size = 1.25)) -> kobe_plot_eng
```

```{r}
ggsave(plot = kobe_plot_eng, "../J-League 2018/output/kobe_plotENG.png",
       height = 6, width = 8)
```

```{r}
plot_logo <- add_logo(plot_path = "../J-League 2018/output/kobe_plotENG.png",
                      logo_path = "https://upload.wikimedia.org/wikipedia/en/8/87/VisselKobe.png",
                      logo_position = "top right",
                      logo_scale = 20)

plot_logo
```

```{r}
image_write(image = plot_logo, "../J-League 2018/output/kobe_logo_plotENG.png")
```


# FC Tokyo
## scrape Tokyo

```{r}
session <- bow("https://www.transfermarkt.com/fc-tokyo/leistungsdaten/verein/6631/plus/0?reldata=JAP1%262017")

print(session)
# "The path is scrapable for this user-agent": OK, looks like we are good to go!

# scraping tranfermarkt is a nightmare...
# scrape each col individually then combine later...

# grab name from photo element instead
result_name <- scrape(session) %>% 
  html_nodes("#yw1 .bilderrahmen-fixed") %>% 
  html_attr("title") 

# grab age
result_age <- scrape(session) %>% 
  html_nodes(".posrela+ .zentriert") %>% 
  html_text()

# grab minutes played in league
result_mins <- scrape(session) %>% 
  html_nodes("td.rechts") %>% 
  html_text()
```

## clean tokyo

```{r}
# place each vector into list

resultados <- list(result_name, result_age, result_mins)

col_name <- c("name", "age", "minutes")

# then reduce(cbind) to combine them, set names to cols 
resultados %>% 
  reduce(cbind) %>% 
  as_tibble() %>% 
  set_names(col_name) -> results_comb

# NOICE.gif
glimpse(results_comb)

# fix "strings" into proper formats, calculate % of minutes appeared
tokyo_minutes <- results_comb %>% 
  
  mutate(age = as.numeric(age),
         minutes = minutes %>% 
           str_replace("\\.", "") %>% 
           str_replace("'", "") %>% 
           as.numeric(),
         min_perc = (minutes / 3060) %>% round(digits = 3)) %>% 
  
  filter(!is.na(minutes)) %>% 
  
  separate(name, into = c("first_name", "last_name"), by = " ") %>%
  # manually fix somes names
  mutate(last_name = case_when(
    first_name == "Lins" ~ "Lins",
    first_name == "Hyeon" ~ "H.S. Jang",
    TRUE ~ last_name)) %>%
  
  arrange(desc(min_perc))

# rectanglular highlight for players in their prime:
rect_df <- data.frame(
  xmin = 26, xmax = 31,
  ymin = -Inf, ymax = Inf
)

glimpse(tokyo_minutes)
```

## plot Tokyo

```{r fig.height=6, fig.width=8}
tokyo_minutes %>% 
  ggplot(aes(x = age, y = min_perc)) +
  geom_vline(xintercept = 25, alpha = 0.4, color = "grey20") +
  geom_hline(yintercept = 0.5, alpha = 0.4, color = "grey20") +
  geom_mark_rect(aes(filter = age >= 26 & age <= 31), 
                 description = "ピーク年齢*", con.cap = 0,
                 color = NA, fill = "#271672", alpha = 0.5) + 
  geom_point(color = "#DD2220", size = 2.5) +
  geom_text_repel(
    aes(label = last_name, family = "Roboto Condensed"),
    nudge_x = 0.5,
    seed = 6) + 
  scale_y_continuous(
    expand = c(0.01, 0),
    limits = c(0, 1), 
    labels = percent_format()) +
  scale_x_continuous(
    breaks = pretty_breaks(n = 10)) +
  labs(
    x = "年齢", 
    y = tategaki_alt("出場時間（％）"),  
    title = "FC東京: 年齢-出場時間プロット",
    subtitle = "J-League 2018 Season (100% = 3060分)",
    caption = glue("
                   データ: transfermarkt.com
                   *主観
                   作: @R_by_Ryo")) +
  theme_bw() +
  theme(
    text = element_text(family = "Roboto Condensed"),
    panel.border = element_rect(color = "#271672", size = 1.25),
    plot.title = element_text(color = "#271672", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "#DD2220", size = 14),
    axis.title.y = element_text(angle = 0, vjust= 0.5),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12)) -> fctokyo_plot
```

```{r}
ggsave(plot = fctokyo_plot, "../J-League 2018/output/fctokyo_plot.png",
       height = 6, width = 8)
```



```{r}
plot_logo <- add_logo(plot_path = "../J-League 2018/output/fctokyo_plot.png",
                      logo_path = "https://upload.wikimedia.org/wikipedia/en/4/45/FCTokyo.png",
                      logo_position = "top right",
                      logo_scale = 18)

plot_logo
```

```{r}
image_write(image = plot_logo, "../J-League 2018/output/fctokyo_logo_plot.png")
```



# Shonan Bellmare 2019

## scrape

```{r}
# https://www.transfermarkt.com/shonan-bellmare/leistungsdaten/verein/8457/plus/0?reldata=JAP1%262018
session <- bow("https://www.transfermarkt.com/shonan-bellmare/leistungsdaten/verein/8457/plus/0?reldata=JAP1%262018")

print(session)
# "The path is scrapable for this user-agent": OK, looks like we are good to go!

# scraping tranfermarkt is a nightmare...
# scrape each col individually then combine later...

# grab name from photo element instead
result_name <- scrape(session) %>% 
  html_nodes("#yw1 .bilderrahmen-fixed") %>% 
  html_attr("title") 

# grab age
result_age <- scrape(session) %>% 
  html_nodes(".posrela+ .zentriert") %>% 
  html_text()

# grab minutes played in league
result_mins <- scrape(session) %>% 
  html_nodes("td.rechts") %>% 
  html_text()
```


## clean

- NEED TO UPDATE AFTER EVERYMATCH DAY (ex. 3 Matches = 270 min >>> 4 Matches = 360 Min)

```{r}
# place each vector into list

resultados <- list(result_name, result_age, result_mins)

col_name <- c("name", "age", "minutes")

# then reduce(cbind) to combine them, set names to cols 
resultados %>% 
  reduce(cbind) %>% 
  as_tibble() %>% 
  set_names(col_name) -> results_comb

# NOICE.gif
glimpse(results_comb)

# fix "strings" into proper formats, calculate % of minutes appeared
shonan_minutes <- results_comb %>% 
  
  mutate(age = as.numeric(age),
         minutes = minutes %>% 
           str_replace("\\.", "") %>% 
           str_replace("'", "") %>% 
           as.numeric(),
         min_perc = (minutes / 360) %>% round(digits = 3)) %>% 
  
  filter(!is.na(minutes)) %>% 
  
  separate(name, into = c("first_name", "last_name"), by = " ") %>%
  ## manually fix somes names
  mutate(last_name = case_when(
    first_name == "Freire" ~ "Freire",
    TRUE ~ last_name)) %>%
  
  arrange(desc(min_perc))

# rectanglular highlight for players in their prime:
rect_df <- data.frame(
  xmin = 26, xmax = 31,
  ymin = -Inf, ymax = Inf
)

glimpse(shonan_minutes)
```


## plot


```{r fig.height=6, fig.width=8}
shonan_minutes %>% 
  ggplot(aes(x = age, y = min_perc)) +
  geom_vline(xintercept = 25, alpha = 0.4, color = "grey20") +
  geom_hline(yintercept = 0.5, alpha = 0.4, color = "grey20") +
  # geom_rect(
  #   data = rect_df, inherit.aes = FALSE,
  #   aes(xmin = xmin, xmax = xmax, 
  #       ymin = ymin, ymax = ymax),
  #   alpha = 0.5,
  #   fill = "#67B356") +
  geom_mark_rect(aes(filter = age >= 26 & age <= 31), 
                 description = "ピーク年齢*", con.cap = 0,
                 color = NA, fill = "#67B356", alpha = 0.5, size = 0.01) +
  geom_point(color = "#103C95", size = 2.5) +
  geom_text_repel(
    aes(label = last_name, family = "Roboto Condensed"),
    nudge_x = 0.5,
    seed = 6) + 
  scale_y_continuous(
    expand = c(0.01, 0),
    limits = c(0, 1.05), 
    labels = percent_format()) +
  scale_x_continuous(
    breaks = pretty_breaks(n = 10)) +
  labs(
    x = "年齢 (3月22日2019年)", 
    y = tategaki_alt("出場時間（％）"), 
    title = "湘南ベルマーレ: 年齢-出場時間プロット",
    subtitle = "J-League 2019 Season (4節: 100% = 360分)",
    caption = glue("
                   データ: transfermarkt.com
                   *主観
                   作: @R_by_Ryo")) +
  theme_bw() +
  theme(
    text = element_text(family = "Roboto Condensed"),
    #panel.grid.minor.y = element_blank(),
    panel.border = element_rect(color = "#67B356", size = 1.25),
    plot.title = element_text(color = "#67B356", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "#103C95", size = 14),
    axis.title.y = element_text(angle = 0, vjust= 0.5),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12)) -> shonan_plot
```




```{r}
ggsave(plot = shonan_plot, "../J-League 2018/output/shonan_plot.png",
       height = 6, width = 8)
```



```{r}
plot_logo <- add_logo(plot_path = "../J-League 2018/output/shonan_plot.png",
                      logo_path = "https://upload.wikimedia.org/wikipedia/en/2/2c/ShonanBellmare.png",
                      logo_position = "top right",
                      logo_scale = 20)

plot_logo
```

```{r}
image_write(image = plot_logo, "../J-League 2018/output/shonan_logo_plot.png")
```



# Shimizu S-Pulse

## scrape

```{r}
# https://www.transfermarkt.com/shonan-bellmare/leistungsdaten/verein/8457/plus/0?reldata=JAP1%262018
session <- bow("https://www.transfermarkt.com/shimizu-s-pulse/leistungsdaten/verein/1062/plus/0?reldata=JAP1%262017")

print(session)
# "The path is scrapable for this user-agent": OK, looks like we are good to go!

# scraping tranfermarkt is a nightmare...
# scrape each col individually then combine later...

# grab name from photo element instead
result_name <- scrape(session) %>% 
  html_nodes("#yw1 .bilderrahmen-fixed") %>% 
  html_attr("title") 

# grab age
result_age <- scrape(session) %>% 
  html_nodes(".posrela+ .zentriert") %>% 
  html_text()

# grab minutes played in league
result_mins <- scrape(session) %>% 
  html_nodes("td.rechts") %>% 
  html_text()
```


## clean

- NEED TO UPDATE AFTER EVERYMATCH DAY (ex. 3 Matches = 270 min >>> 4 Matches = 360 Min)

```{r}
# place each vector into list

resultados <- list(result_name, result_age, result_mins)

col_name <- c("name", "age", "minutes")

# then reduce(cbind) to combine them, set names to cols 
resultados %>% 
  reduce(cbind) %>% 
  as_tibble() %>% 
  set_names(col_name) -> results_comb

# NOICE.gif
glimpse(results_comb)

# fix "strings" into proper formats, calculate % of minutes appeared
shimizu_minutes <- results_comb %>% 
  
  mutate(age = as.numeric(age),
         minutes = minutes %>% 
           str_replace("\\.", "") %>% 
           str_replace("'", "") %>% 
           as.numeric(),
         min_perc = (minutes / 3060) %>% round(digits = 3)) %>% 
  
  filter(!is.na(minutes)) %>% 
  
  separate(name, into = c("first_name", "last_name"), by = " ") %>%
  ## manually fix somes names
  mutate(last_name = case_when(
    first_name == "Freire" ~ "Freire",
    first_name == "Crislan" ~ "Crislan",
    first_name == "Douglas" ~ "Douglas",
    first_name == "Seok" ~ "S.H. Hwang",
    TRUE ~ last_name)) %>%
  
  arrange(desc(min_perc))

# rectanglular highlight for players in their prime:
rect_df <- data.frame(
  xmin = 26, xmax = 31,
  ymin = -Inf, ymax = Inf
)

glimpse(shimizu_minutes)
```


## plot
- lighter blue: #0D6BA5
- lightish blue: #0569AE
- orange: #F29900

```{r fig.height=6, fig.width=8}
shimizu_minutes %>% 
  ggplot(aes(x = age, y = min_perc)) +
  geom_vline(xintercept = 25, alpha = 0.4, color = "grey20") +
  geom_hline(yintercept = 0.5, alpha = 0.4, color = "grey20") +
  geom_mark_rect(aes(filter = age >= 26 & age <= 31), 
                 description = "ピーク年齢*", con.cap = 0,
                 color = NA, fill = "#F29900", alpha = 0.5, size = 0.01) +
  geom_point(color = "#0569AE", size = 2.5) +
  geom_text_repel(
    aes(label = last_name, family = "Roboto Condensed"),
    nudge_x = 0.5,
    seed = 6) + 
  scale_y_continuous(
    expand = c(0.01, 0),
    limits = c(0, 1.05), 
    labels = percent_format()) +
  scale_x_continuous(
    breaks = pretty_breaks(n = 10)) +
  labs(
    x = "年齢 (3月22日2019年)", 
    y = tategaki_alt("出場時間（％）"), 
    title = "清水エスパルス: 年齢-出場時間プロット",
    subtitle = "J-League 2018 Season (100% = 3060分)",
    caption = glue("
                   *主観
                   データ: transfermarkt.com
                   作: @R_by_Ryo")) +
  theme_bw() +
  theme(
    text = element_text(family = "Roboto Condensed"),
    panel.border = element_rect(color = "#F29900", size = 1.25),
    plot.title = element_text(color = "#F29900", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "#0569AE", size = 14),
    axis.title.y = element_text(angle = 0, vjust= 0.5),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12)) -> shimizu_plot
```




```{r}
ggsave(plot = shimizu_plot, "../J-League 2018/output/shimizu_plot.png",
       height = 6, width = 8)
```



```{r}
plot_logo <- add_logo(plot_path = "../J-League 2018/output/shimizu_plot.png",
                      logo_path = "https://upload.wikimedia.org/wikipedia/en/4/4c/ShimizuS-Pulse.png",
                      logo_position = "top right",
                      logo_scale = 20)

plot_logo
```

```{r}
image_write(image = plot_logo, "../J-League 2018/output/shimizu_logo_plot.png")
```

### english version


```{r fig.height=6, fig.width=8}
shimizu_minutes %>% 
  ggplot(aes(x = age, y = min_perc)) +
  geom_vline(xintercept = 25, alpha = 0.4, color = "grey20") +
  geom_hline(yintercept = 0.5, alpha = 0.4, color = "grey20") +
  geom_mark_rect(aes(filter = age >= 26 & age <= 31), 
                 description = "Prime Age*", con.cap = 0,
                 color = NA, fill = "#F29900", alpha = 0.5, size = 0.01) +
  geom_point(color = "#0569AE", size = 2.5) +
  geom_text_repel(
    aes(label = last_name, family = "Roboto Condensed"),
    nudge_x = 0.5,
    seed = 6) + 
  scale_y_continuous(
    expand = c(0.01, 0),
    limits = c(0, 1.05), 
    labels = percent_format()) +
  scale_x_continuous(
    breaks = pretty_breaks(n = 10)) +
  labs(
    x = "Current Age (As of March 30, 2019)", 
    y = "% of Minutes Played", 
    title = "Shimizu S-Pulse: Age-Utility Matrix",
    subtitle = "J-League 2018 Season (100% = 3060 minutes)",
    caption = glue("
                   *Subjective
                   Data: transfermarkt.com
                   Created by: @R_by_Ryo")) +
  theme_bw() +
  theme(
    text = element_text(family = "Roboto Condensed"),
    panel.border = element_rect(color = "#F29900", size = 1.25),
    plot.title = element_text(color = "#F29900", size = 16, face = "bold"),
    plot.subtitle = element_text(color = "#0569AE", size = 14),
    #axis.title.y = element_text(angle = 0, vjust= 0.5),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12)) -> shimizu_plot_eng
```




```{r}
ggsave(plot = shimizu_plot_eng, "../J-League 2018/output/shimizu_plotENG.png",
       height = 6, width = 8)
```



```{r}
plot_logo <- add_logo(plot_path = "../J-League 2018/output/shimizu_plotENG.png",
                      logo_path = "https://upload.wikimedia.org/wikipedia/en/4/4c/ShimizuS-Pulse.png",
                      logo_position = "top right",
                      logo_scale = 20)

plot_logo
```

```{r}
image_write(image = plot_logo, "../J-League 2018/output/shimizu_logo_plotENG.png")
```
